\documentclass[sigconf,nonacm=false]{acmart}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{tikz}

\begin{document}
\title{The Behavioral Ceiling: Eight AI Agent Categories Are Classifiable but Not Discoverable from On-Chain Transaction Features Alone}
\author{NSF Project Team}
\affiliation{\institution{University}\country{USA}}

\begin{abstract}
We formalize four necessary-and-sufficient conditions (C1--C4) for on-chain AI agency and derive an eight-category taxonomy spanning 2,744 Ethereum addresses.
The paper reports both positive and negative results.
\textbf{Positive:} Supervised classification achieves 92.1\% accuracy (8-class) and 95.3\% with cross-study features---the taxonomy \emph{is} learnable given labeled data.
Five-class accuracy reaches 97.4\%; four of eight classes exceed F1\,0.85 even in the full eight-class setting.
\textbf{Negative (the behavioral ceiling):} Unsupervised methods find only 2--3 natural clusters (K-Means silhouette peaks at $k{=}3$; HDBSCAN identifies 2 density clusters), not the eight that the taxonomy defines.
The eight categories are not \emph{discoverable} from behavior alone---they require provenance metadata.
Cross-study feature transfer from an independent sybil-detection study (31 features total) lifts Bridge F1 from 0.31 to 0.76 and DAO F1 from 0.14 to 0.43, showing the ceiling can be raised selectively---yet LLM-Powered Agents remain stubbornly hard to recall against rule-based DeFi Management Agents (F1\,=\,0.44; precision 0.80, recall 0.39).
However, we show the ceiling is penetrable: 16 decision-process features capturing error recovery behavior, session patterns, nonce regularity, and gas pricing microstructure raise LLM-Powered Agent F1 from 0.38 to 0.53 (+15.3\,pp).
Full-scale analysis of inter-transaction reaction times finds Cohen's $d{=}1.01$ for general reaction time---the largest effect size in our 54-feature set---suggesting that LLM inference latency creates a physically unconcealable behavioral signature.
A 200-address pilot had suggested DeFi-specific reaction time as the primary driver ($d{=}1.25$), but full-scale replication on 2,744 addresses (936K DeFi transactions) attributes the signal to general timing patterns ($d{=}1.01$), not DeFi-specific interactions; the DeFi-specific feature did not replicate ($d{\approx}0$).
This distinction between classifiability and discoverability has direct regulatory implications: a supervised detector \emph{can} be trained, but it cannot be deployed without a labeled training set from each target chain and time period.
Any purely behavioral regulatory framework that lacks provenance labels can at most distinguish ``automated high-frequency'' from ``manual low-frequency'' activity---it cannot isolate LLM-powered, RL-driven, or DAO-governed agents from their rule-based counterparts.
\end{abstract}

\keywords{AI agents; Web3; decentralized finance; agent definition; behavioral taxonomy; on-chain analytics; cluster validation; multi-class classification.}

\maketitle

\section{The Behavioral Ceiling: Eight AI Agent Categories Are Classifiable but Not Discoverable}

\textbf{Paper 0 --- NSF AI Agent Project}



\section{1. Introduction}

Can we tell eight types of on-chain AI agents apart by watching their transactions? This paper's answer is \textit{yes, if you have labeled training data}---and \textit{no, if you must discover the categories from behavior alone}. The gap between these two answers matters for regulators, researchers, and platform designers alike.

AI agents have quietly become first-class participants in the decentralized-finance (DeFi) economy. From Maximal Extractable Value (MEV) bots harvesting arbitrage opportunities to Autonolas services rebalancing yield-farming positions, from cross-chain relayers bridging assets to DAO execution modules settling governance decisions, software entities now autonomously manage many billions of dollars of crypto assets. Flashbots alone reports that MEV extraction on Ethereum has surpassed USD 600 million since 2020, almost entirely performed by automated programs.

Yet ``AI agent'' is applied indiscriminately to a scheduled payout cron, a grid-trading bot, and an LLM-driven policy engine that re-reasons its DeFi positions every block. This terminological flattening obstructs three things the HCI and systems communities care about: \textbf{measurement} (we cannot count what we cannot define), \textbf{comparison} (we cannot say one class of agent behaves differently from another if we do not distinguish them), and \textbf{governance} (a regulator cannot impose differentiated disclosure requirements on ``the agent'' when the same word names a cron job and an LLM). Classical AI offers definitional scaffolding but not measurable criteria. Russell and Norvig's [2020] perceive-and-act schema is broad enough to include thermometers. Wooldridge and Jennings's [1995] autonomy / social ability / reactivity / pro-activeness tetrad is implementation-neutral and cannot be checked against public transaction data. The blockchain bot literature [Daian et al. 2020; Qin et al. 2022; Torres et al. 2021] documents behavior in exquisite detail but rarely links its findings back to formal agent theory, lumping ``anything automated'' under ``bot''.

We therefore set out to build the missing infrastructure: a formal definition (C1--C4), an eight-category taxonomy, and a progressive empirical validation on 2,744 Ethereum addresses. What we discovered is that the taxonomy is both stronger and weaker than expected---strong for \textbf{supervised classification} (92.1\% eight-class accuracy), but weak for \textbf{unsupervised discovery}. The experiments reveal both a positive result and a \textbf{behavioral ceiling}:

\begin{itemize}
\item \textbf{Step 1: Unsupervised clustering (the ceiling).} K-Means silhouette peaks at $k{=}3$; HDBSCAN finds only 2 density clusters. Without labels, the 23-feature behavioral space contains at most three natural groups, not eight. The eight categories are not \emph{discoverable} from behavior alone.
\item \textbf{Step 2: Five-class classification (strong).} A Gradient Boosting classifier achieves 97.4\% accuracy on five categories---four of five classes exceed F1\,0.85. Only LLM-Powered Agents show cracks (F1\,=\,0.47), with 60\% misclassified as DeFi Management Agents.
\item \textbf{Step 3: Eight-class classification (strong overall, weak on minority classes).} Expanding to all eight categories achieves 92.1\% accuracy---a strong result overall. Macro-F1 falls to 0.58 because four small or overlapping classes are weak, but the four dominant classes remain above F1\,0.91.
\item \textbf{Step 4: Cross-study feature transfer (targeted improvement).} Adding eight AI-detection features from an independent sybil study lifts overall accuracy to 95.3\%, with Bridge F1 from 0.31 to 0.76 and DAO F1 from 0.14 to 0.43---the ceiling \emph{can} be raised selectively. But LLM-Powered Agents remain stubbornly at F1\,=\,0.44 under transaction-content features alone.
\item \textbf{Step 5: Decision-process features (breakthrough).} Sixteen features capturing error recovery, session dynamics, nonce regularity, and gas pricing microstructure raise LLM-Powered Agent F1 from 0.38 to 0.53 ($+$15.3\,pp) and overall accuracy to 95.6\%. A full-scale study of inter-transaction reaction times finds Cohen's $d{=}1.01$ for general timing---suggesting that LLM inference latency creates a physically unconcealable behavioral signature (a 200-address pilot suggested $d{=}1.25$ for DeFi-specific timing, but this did not replicate at scale).
\end{itemize}

The key distinction is between \textbf{classifiability} and \textbf{discoverability}. The eight categories are real---they are provenance-verified and semantically distinct---and they are \emph{classifiable} with labeled data (92\% accuracy). But they are not \emph{discoverable} from behavior alone: unsupervised methods find three super-clusters, not eight categories. The implication is that a supervised detector can be trained, but it requires labeled training data from each target chain and time period. Any purely behavioral regulatory framework that lacks provenance labels can at most separate ``automated high-frequency'' from ``manual low-frequency'' activity; it cannot isolate LLM-powered, RL-driven, or DAO-governed agents from their rule-based counterparts.

\input{../../shared/figures/fig_pipeline.tex}

\textbf{Research questions.} We frame the investigation around two questions:

\textbf{RQ1.} What formal conditions distinguish an AI agent from a bot, a script, or a human user operating through software, \textit{when the only observation channel is the blockchain itself}?

\textbf{RQ2.} Does a semantically motivated eight-category taxonomy survive contact with real on-chain data---are all eight categories distinguishable from behavioral features? And if not, where exactly does distinguishability break down?

\textbf{Contributions.} Our contributions are both constructive and cautionary:

1. \textbf{A four-condition definition (C1--C4).} On-chain actuation, environmental perception, autonomous decision-making, and adaptiveness are proposed as \textit{necessary and jointly sufficient} for on-chain AI agency. Each condition is justified by a counterexample-based non-redundancy argument (Section 3) and mapped to an operationalization in transaction-level features.

2. \textbf{An eight-category taxonomy.} Agents are classified along three orthogonal dimensions---autonomy level (5 ranks), environment type (4 types), decision model (5 types)---yielding eight disjoint categories that cover both agents (5 classes) and non-agent baselines (2 classes) plus one boundary class (cross-chain bridges).

3. \textbf{A progressive empirical characterization of classifiability vs.\ discoverability.} Rule-based projection, K-Means cluster sweep, five-class and eight-class supervised classifiers, and cross-study feature expansion on 2,744 Ethereum addresses jointly reveal that (a)~supervised classification achieves 92\% eight-class accuracy, proving the categories are behaviorally distinct when labels are available, while (b)~unsupervised methods saturate at 2--3 clusters, not 8, showing the categories are not discoverable from behavior alone.

4. \textbf{Two positive findings, three negative findings, and a breakthrough with governance implications.} \textit{Positive:} Supervised classification at 92\% accuracy (eight-class) proves the taxonomy categories are behaviorally distinct---a labeled detector is feasible. \textit{Negative:} (a)~The behavioral silhouette is maximized at $k{=}3$, not $k{=}8$: without labels, the eight categories are not discoverable. (b)~LLM-Powered Agents have low recall against DeFi Management Agents under transaction-content features (F1\,=\,0.44; precision 0.80 but recall only 0.39). (c)~Cross-study features help Bridge and DAO classes substantially but cannot resolve the LLM/DeFi boundary with transaction-content features alone. \textit{Breakthrough:} Decision-process features raise LLM-Powered F1 from 0.38 to 0.53 ($+$15.3\,pp); full-scale reaction-time analysis finds Cohen's $d{=}1.01$ for general inter-transaction timing, suggesting LLM inference latency is a physically unconcealable signal (a pilot's DeFi-specific $d{=}1.25$ did not replicate at scale).

5. \textbf{Transparent threats to validity.} The taxonomy projection rules reuse eight of the 23 features, creating a known partial circularity. We quantify this risk and discuss its implications.

The paper proceeds as follows. Section 2 reviews related definitions. Section 3 formalizes C1--C4 and argues for their non-redundancy. Section 4 presents the progressive validation---framed as a progressive exposure of, and breakthrough beyond, the behavioral ceiling. Section 5 discusses what the ceiling means for regulators, researchers, and the taxonomy itself. Section 6 treats limitations, and Section 7 concludes.


\section{2. Background and Related Work}

Four strands of prior work inform our framing: classical AI-agent definitions, HCI automation-level work, blockchain bot and MEV empirical work, and emerging on-chain AI-agent platforms. Table 1 positions our definition against the major prior proposals.

\textbf{Table 1. Agent definitions and their coverage of the four conditions used in this paper.} Check-marks indicate that the prior work explicitly or implicitly includes the listed condition; dashes indicate it is omitted or assumed. \textit{C1 = on-chain actuation; C2 = environmental perception; C3 = autonomous decision-making; C4 = adaptiveness.}

\begin{table}[h]
\centering
\small
\begin{tabular}{llllllll}
\toprule
Work & Year & Discipline & C1 & C2 & C3 & C4 & Web3 applicable? \\
\midrule
Russell \& Norvig [2020] & 2020 & AI textbook & --- & $\checkmark$ & partial & --- & too broad (thermometers qualify) \\
Wooldridge \& Jennings [1995] & 1995 & Multi-agent systems & --- & $\checkmark$ & $\checkmark$ & $\checkmark$ & no actuation spec \\
Franklin \& Graesser [1996] & 1996 & Taxonomy & --- & $\checkmark$ & $\checkmark$ & $\checkmark$ & property enumeration, not necessity \\
Maes [1995] & 1995 & Artificial life & --- & $\checkmark$ & $\checkmark$ & $\checkmark$ & no persistence criterion \\
Shoham [1993] & 1993 & Agent programming & --- & --- & $\checkmark$ & --- & requires BDI layer \\
Dennett [1987] & 1987 & Philosophy & --- & $\checkmark$ & $\checkmark$ & --- & observer-dependent \\
Park et al. [2023] & 2023 & NLP / HCI & --- & $\checkmark$ & $\checkmark$ & $\checkmark$ & text simulacra, not Web3 \\
Chan et al. [2023] & 2023 & AI safety & --- & $\checkmark$ & $\checkmark$ & --- & counterfactual influence \\
Shavit et al. [2023] & 2023 & Governance & --- & $\checkmark$ & $\checkmark$ & --- & no actuation spec \\
Autonolas whitepaper [2022] & 2022 & Web3 engineering & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & native \\
Eliza / AI16Z docs [2024] & 2024 & Web3 engineering & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & native \\
\textbf{This paper (C1-C4)} & 2026 & Web3 systems & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & native \\
\bottomrule
\end{tabular}
\end{table}

\subsection{2.1 Classical AI-agent definitions}

Russell and Norvig [2020] define an agent as "anything that can be viewed as perceiving its environment through sensors and acting upon that environment through actuators." This is the weakest possible framing --- a thermostat satisfies it. Their book refines the notion via architectural tiers (simple reflex, model-based, goal-based, utility-based, learning), tiers that inspired our autonomy dimension. Wooldridge and Jennings [1995] advance four attributes for \textit{intelligent} agents: autonomy, social ability, reactivity, and pro-activeness. We retain autonomy (C3), reactivity (C2), and pro-activeness (~C4) but drop social ability, because a lone MEV bot is uncontroversially an agent. Franklin and Graesser [1996] enumerate candidate properties (reactive, autonomous, goal-oriented, temporally continuous, communicative, learning, mobile, flexible, character) without committing to necessity; our C1-C4 are a specific minimal necessary subset. Maes [1995] argues for \textit{behavioral} definition --- agents should be identified by observable behavior, not architecture. This philosophical stance is the foundation of our operationalization in Section 3.3.

\subsection{2.2 HCI automation-level work}

Shneiderman [2022] argues against framing full autonomy as the design goal, proposing a two-dimensional human-control / computer-automation framework. Parasuraman, Sheridan, and Wickens [2000] offer a 10-level classification across four information-processing stages (acquisition, analysis, decision, action); we collapse this to a 5-level autonomy dimension because transaction data exposes only action, not internal processing stages. Amershi et al. [2019] distill 18 guidelines for human-AI interaction relevant to how agents present themselves to users, but they do not address \textit{measurement}. Horvitz [1999] formalizes mixed-initiative interaction; our collaborative autonomy level inherits this framing for DAO-gated agents.

\subsection{2.3 Blockchain bot and MEV empirics}

Daian et al. [2020] are the canonical reference for the measurement of on-chain automated agents. Their "Flash Boys 2.0" paper quantifies priority-gas auctions, front-running, and sandwich attacks, and establishes that a substantial fraction of DEX volume is driven by automated programs. Qin, Zhou, and Gervais [2022] extend this to quantify extractable value across DeFi protocols. Torres et al. [2021] contribute a USENIX Security empirical study that itemizes the behavioral fingerprints of front-runners (gas-price sequences, timing relative to target transactions). All three works treat automation as a single undifferentiated category --- "bots" --- and do not distinguish between what we will call Deterministic Scripts, Simple Trading Bots, MEV Searchers, and DeFi Management Agents. Our taxonomy provides the missing granularity.

\subsection{2.4 On-chain AI-agent platforms}

Autonolas / OLAS [Autonolas 2022] provides an open-source multi-agent service framework in which agents stake OLAS to register, settle off-chain computation on-chain through a finite-state machine, and expose their activity in a public registry. This is the most important training-data source for our rule-based projection (Section 4.2). AI16Z / Eliza [2024] packages LLM reasoning into an on-chain persona that can trade, post on social media, and interact with DeFi protocols; it is the canonical example of what we call an LLM-Powered Agent. Virtuals Protocol tokenizes agents, linking each agent to a token reflecting its utility. Fetch.ai's Autonomous Economic Agents (AEAs) formalize peer-to-peer agent communication. These platforms commit to "agent" as a design category but do not share a definition that lets a third party audit claims.

\subsection{2.5 Gaps}

Three gaps motivate this paper:

1. \textbf{No existing definition ties agent-ness to on-chain observability.} Architectural definitions (BDI, FSM, RL policy) are not directly checkable from blockchain data. We need a definition whose conditions can be evaluated on transaction logs.

2. \textbf{No existing definition separates "has a policy" from "adapts its policy".} Wooldridge's pro-activeness and Franklin and Graesser's goal-orientation both admit frozen-strategy bots as agents. Our C4 (adaptiveness) enforces learning over time.

3. \textbf{No existing taxonomy of on-chain agents is empirically validated.} Prior taxonomies are internal and self-consistent but have not been projected onto real data. Blockchain's full-record property is a unique opportunity for empirical validation, which Section 4 of this paper exercises.


\section{3. The C1-C4 Definition}

This section presents a formal statement of the four-condition definition, justifies each condition by a counterexample demonstrating its non-redundancy, and describes how each condition is operationalized on transaction-level features.

\subsection{3.1 Formal statement}

\textbf{Definition (On-chain AI agent).} Let $E$ be a software entity and let $B$ be the sequence of blockchain events associated with $E$ over a time window $[t_0, t_1]$. Then $E$ is an on-chain AI agent iff it satisfies all four conditions:

$$
\mathrm{Agent}(E) \iff C\_1(E) \land C\_2(E) \land C\_3(E) \land C\_4(E).
$$

\textbf{C1 --- On-chain actuation.}
$$
C\_1(E) \iff \mathrm{Control}(E, \alpha) \text{ where } \alpha \text{ is an EOA and } \exists\,\mathrm{tx} \in B : \mathrm{tx.from} = \alpha.
$$
$E$ directly or indirectly controls an externally-owned account $\alpha$, and $\alpha$ initiates at least one transaction in the observation window.

\textbf{C2 --- Environmental perception.}
$$
C\_2(E) \iff I(\mathrm{state}\_t ;\, \mathrm{action}\_{t+1}) > 0,
$$
where $I$ is the mutual information between the chain state at time $t$ (and any off-chain signals observable by $E$) and the parameters of the next transaction.

\textbf{C3 --- Autonomous decision-making.}
$$
C\_3(E) \iff H(\mathrm{action} \mid \mathrm{environment}) > 0 \;\land\; \lnot\,\mathrm{human\text{-}gated}(E).
$$
The conditional entropy of actions given environment is positive (there is genuine non-determinism) \textit{and} each individual transaction is not preceded by a per-transaction human approval signal.

\textbf{C4 --- Adaptiveness.}
$$
C\_4(E) \iff \exists\,\text{window } w :\; \mathrm{KS\text{-}dist}\!\left(\mathrm{params}\_{t \leq w},\, \mathrm{params}\_{t > w}\right) > \delta.
$$
Some behavioral-parameter distribution drifts by more than a Kolmogorov-Smirnov threshold between an early and a late sub-window.

\subsection{3.2 Non-redundancy: each condition excludes a distinct counterexample}

Each $C_i$ excludes a class of entities that satisfy the other three. We present one counterexample per condition.

\textbf{$C_1$ is non-redundant --- smart contracts.} A Uniswap V3 pool reacts to calldata ($C_2$), its output curve is non-trivial for varied inputs ($C_3$-like), and its fee tier can evolve via governance ($C_4$). But it cannot initiate transactions --- it is only callable. Removing $C_1$ would admit every non-trivial contract as an agent.

\textbf{$C_2$ is non-redundant --- blind relayers.} An entity that signs pre-computed transaction batches and submits them on a fixed schedule without reading chain state satisfies $C_1$ (EOA), and its inter-transaction interval has positive variance due to mempool latency ($\sim C_3$), and its batch sizes drift due to external queue dynamics ($\sim C_4$). But its transaction parameters are not conditioned on chain state; $C_2$ would be violated by construction. Removing $C_2$ would admit every scheduled relayer.

\textbf{$C_3$ is non-redundant --- deterministic DCA bots.} A grid / DCA trading bot has an EOA ($C_1$), reads price before each trade ($C_2$), and may have its grid width parameter-tuned by its owner ($C_4$). But given the same price it always executes the same trade --- conditional entropy is zero. Removing $C_3$ would admit every DCA bot.

\textbf{$C_4$ is non-redundant --- frozen MEV sandwich bots.} A bot that runs exactly the same sandwich logic from deployment to deprecation has an EOA ($C_1$), observes the mempool ($C_2$), and is non-deterministic in which mempool target it chooses ($C_3$). But its sandwich parameters (slippage, gas strategy, target selection) never change. Removing $C_4$ would admit frozen-strategy bots, losing a key property of \textit{intelligent} agency: the ability to learn from experience.

\subsection{3.3 Operationalization on transaction-level features}

The four conditions are latent --- we cannot inspect the source code or the internal decision graph of an entity from its blockchain footprint alone. We propose the following observable proxies, which form the theoretical grounding for the 23-feature set shared with Paper 1:

- \textbf{C1 is observable from:} \texttt{eth\_getCode(address) == "0x"} (the address is an EOA, not a contract) and the existence of at least one transaction with \texttt{from == address}.

- \textbf{C2 is observable from:} calldata entropy > 0 (diverse method calls indicate reaction to environment), short latency between on-chain events and subsequent transactions relative to a fixed schedule, and positive correlation between transaction timing and on-chain event timing.

- \textbf{C3 is observable from:} \texttt{tx\_interval\_cv} above a threshold (non-deterministic timing), \texttt{active\_hour\_entropy > 2.5} or \texttt{burst\_ratio > 0.05} (non-circadian or humanly-impossible burst patterns).

- \textbf{C4 is observable from:} \texttt{gas\_strategy\_drift > 0.15} between early and late sub-windows, Jaccard change of the target-contract set above a threshold, and detectable strategy switch points via changepoint analysis.

Table 2 summarizes the observability of each condition.

\textbf{Table 2. Observability and robustness of C1-C4 proxies.}

\begin{table}[h]
\centering
\small
\begin{tabular}{llll}
\toprule
Condition & Robustness & Primary proxy & False-positive sources \\
\midrule
$C_1$ & high & \texttt{eth\_getCode}, outgoing tx count & multisig-controlled contracts \\
$C_2$ & medium & calldata entropy, event-driven latency & pre-computed batched txs \\
$C_3$ & low & tx-interval CV, hour entropy, burst ratio & heavy human DeFi users \\
$C_4$ & low & distributional drift, KS-distance & external market regime shifts \\
\bottomrule
\end{tabular}
\end{table}

\textbf{A critical caveat on label leakage.} If the $C_3$ proxies (\texttt{tx\_interval\_cv}, \texttt{active\_hour\_entropy}, \texttt{burst\_ratio}) are used both as \textit{labeling gates} (to decide which addresses are agents) and as \textit{classifier features} (to learn an agent-vs-human separator), the classifier exhibits direct target leakage. The formal definition above is independent of this: $C_3$ requires the \textit{concept} of non-determinism and non-human-gating. For downstream use in Paper 1, labels are derived from external provenance (platform registry membership, Flashbots searcher list, ENS) and the 23 features are used only to test how well the concept is \textit{recoverable} from behavior, not to define the label.

\subsection{3.4 Boundary cases}

Some entities occupy the boundary of the definition; we treat them explicitly rather than hide them behind an arbitrary threshold.

\textbf{Cross-chain bridge relayers.} Pass $C_1$ (EOA) and $C_2$ (monitor both chains). $C_3$ is partial (deterministic relay logic, but timing can be stochastic). $C_4$ is partial (parameters updated off-chain by operators). Paper 0 labels these as category 4 with a 0.5 confidence weight.

\textbf{ERC-4337 account-abstraction smart wallets with automation.} Tricky on $C_1$: the smart wallet is not an EOA, but the bundler (or session key) that submits on its behalf is. $C_2$ passes, $C_3$ passes if automation uses learned policy, $C_4$ is variable. Our resolution: the bundler / session-key is the C1 actuator; the smart wallet is a \textit{tool} used by the agent, not the agent.

\textbf{Serial Sybil bots (one operator, many EOAs).} Satisfy $C_1$ per EOA and $C_2$ (read airdrop criteria), but typically fail $C_3$ because all EOAs execute the same playbook and fail $C_4$ because the playbook is static. \textit{This is important for Paper 3: AI Sybils violate $C_3$ because their behavior is coordinated by a single controller, even though the individual EOAs look noisy.}

\textbf{Liquidation bots.} Pass all four: $C_1$ (EOA), $C_2$ (price feeds), $C_3$ (race conditions mean only one wins, which depends on gas strategy), $C_4$ (gas strategies evolve as mempool conditions change). Clear agents.


\section{4. Progressive Validation}

We now project the C1-C4 definition onto a taxonomy with finer semantic granularity, and validate both on real on-chain data. We present results in a progressive structure---from the strongest behavioral signal (3-class super-clusters) through the full 8-class taxonomy---using five complementary methods. Rule-based projection tests whether the taxonomy can be operationalized as a deterministic classifier. Unsupervised clustering tests whether the taxonomy structure is recoverable from behavior alone. Multi-class supervised classification tests whether each category has a learnable behavioral signature. Cross-study feature expansion tests whether adding AI-detection features improves discrimination on weak classes. Finally, decision-process feature engineering tests whether moving from transaction-content to decision-process observation can break through the ceiling.

\subsection{4.1 Validation strategy and dataset}

The base dataset is 2,590 agent addresses from Paper 1's expanded mining (\texttt{features\_expanded.parquet}), spanning Autonolas, Fetch.ai, AI Arena, and curated MEV-searcher lists. We exclude 726 human-labeled addresses from the projection to keep the focus on agent-subtype distinguishability. A Phase~2 targeted mining pass adds 154 addresses for three previously empty categories (DAO $n{=}34$, Bridge $n{=}95$, RL $n{=}25$), yielding $N = 2{,}744$ total for the eight-class experiments (Sections~4.6--4.7). Across all experiments we use at minimum the same 23-feature set (described in Section 3.3 and detailed in Table 3), standardized with z-scoring and winsorized at the [1, 99] percentile range.

\textbf{Table 3. The 23 behavioral features used in Section 4 experiments.}

\begin{table}[h]
\centering
\small
\begin{tabular}{ll}
\toprule
Group & Features \\
\midrule
Timing (7) & tx\_interval\_mean, tx\_interval\_std, tx\_interval\_skewness, active\_hour\_entropy, night\_activity\_ratio, weekend\_ratio, burst\_frequency \\
Gas (6) & gas\_price\_round\_number\_ratio, gas\_price\_trailing\_zeros\_mean, gas\_limit\_precision, gas\_price\_cv, eip1559\_priority\_fee\_precision, gas\_price\_nonce\_correlation \\
Interaction (5) & unique\_contracts\_ratio, top\_contract\_concentration, method\_id\_diversity, contract\_to\_eoa\_ratio, sequential\_pattern\_score \\
Approval (5) & unlimited\_approve\_ratio, approve\_revoke\_ratio, unverified\_contract\_approve\_ratio, multi\_protocol\_interaction\_count, flash\_loan\_usage \\
\bottomrule
\end{tabular}
\end{table}

\subsection{4.2 The eight-category taxonomy}

We organize agent subtypes along three orthogonal dimensions.

- \textbf{Autonomy level (5 ranks):} NONE, REACTIVE, ADAPTIVE, PROACTIVE, COLLABORATIVE.
- \textbf{Environment type (4 types):} on-chain only, hybrid (off-chain to on-chain), cross-chain, multi-modal.
- \textbf{Decision model (5 types):} deterministic, statistical, LLM-driven, reinforcement learning, hybrid.

The Cartesian product has 100 cells, but only a small minority are semantically populated by actual systems. We define eight categories covering the Web3 agent ecosystem as of 2026:

1. \textbf{Deterministic Script} (NONE, hybrid, deterministic) --- scheduled transfers, hard-coded airdrop distributors. \textit{Not an agent under C1-C4.}
2. \textbf{Simple Trading Bot} (REACTIVE, hybrid, deterministic) --- grid, DCA, rule-based rebalancers. \textit{Not an agent under C1-C4.}
3. \textbf{MEV Searcher} (ADAPTIVE, hybrid, statistical) --- sandwich / arbitrage / liquidation. \textit{Agent.}
4. \textbf{Cross-Chain Bridge Agent} (ADAPTIVE, cross-chain, deterministic) --- LayerZero / Wormhole relayers. \textit{Boundary.}
5. \textbf{RL Trading Agent} (ADAPTIVE, hybrid, reinforcement learning). \textit{Agent.}
6. \textbf{DeFi Management Agent} (PROACTIVE, hybrid, hybrid) --- Autonolas services, Yearn strategists, DeFi Saver. \textit{Agent.}
7. \textbf{LLM-Powered Agent} (PROACTIVE, multi-modal, LLM-driven) --- AI16Z / Eliza, Virtuals. \textit{Agent.}
8. \textbf{Autonomous DAO Agent} (COLLABORATIVE, on-chain, hybrid) --- Gnosis Safe modules, Governor execution. \textit{Agent.}

Categories 1-2 are non-agents by C1-C4 and serve as reference baselines. Category 4 is a boundary class. The remaining five --- 3, 5, 6, 7, 8 --- are agents. The taxonomy thus spans both agents and non-agents; the C1-C4 definition draws the boundary \textit{within} the taxonomy between REACTIVE and ADAPTIVE.

\subsection{4.3 Rule-based taxonomy projection}

\textbf{Method.} Each agent in the dataset is assigned to one of the eight categories by a two-tier rule system. Tier 1 uses \textit{provenance}: the contract source from which the address was mined and any name annotation (Etherscan label, ENS resolution, Flashbots searcher list). Tier 2 uses \textit{feature-based refinement}: when provenance is ambiguous, the rule consults a four-dimensional subspace of the behavioral feature set (\texttt{burst\_frequency}, \texttt{gas\_price\_round\_number\_ratio}, \texttt{unique\_contracts\_ratio}, \texttt{multi\_protocol\_interaction\_count}).

Representative Tier 1 rules include: an address mined from the Autonolas Agent Registry maps to DeFi Management Agent with confidence 0.90; a name containing \texttt{MEV|Flashbots|sandwich|builder} maps to MEV Searcher with confidence 0.95; a name containing \texttt{AI Arena NRN} maps to LLM-Powered Agent candidate with confidence 0.75. Representative Tier 2 rules include: \texttt{burst\_frequency > 0.20 $\wedge$ gas\_price\_cv > 0.30} maps to MEV Searcher; \texttt{gas\_price\_round\_number\_ratio > 0.60 $\wedge$ method\_id\_diversity < 1.5} maps to Deterministic Script; \texttt{multi\_protocol\_interaction\_count $\geq$ 5 $\wedge$ unique\_contracts\_ratio > 0.40} maps to DeFi Management Agent. We use a \textit{transparent} rule set rather than a learned mapping, because Section 4.5's classifier will consume the projection as ground truth and we want the relationship to be as non-circular as possible: the projection rules use four features in the refinement layer, the classifier uses all 23.

\textbf{Results.} Table 4 shows the projection.

\textbf{Table 4. Taxonomy projection of the base 2,590 agents (five-class experiments). DAO, Bridge, and RL are populated in the Phase~2 expansion (Section~4.6).}

\begin{table}[h]
\centering
\small
\begin{tabular}{llll}
\toprule
Category & Count & Percentage & Mean confidence \\
\midrule
DeFi Management Agent & 1,669 & 64.4\% & 0.60 \\
Deterministic Script & 666 & 25.7\% & 0.80 \\
Simple Trading Bot & 130 & 5.0\% & 0.70 \\
LLM-Powered Agent & 71 & 2.7\% & 0.60 \\
MEV Searcher & 54 & 2.1\% & 0.85 \\
Autonomous DAO Agent & 0 & 0.0\% & --- \\
Cross-Chain Bridge & 0 & 0.0\% & --- \\
RL Trading Agent & 0 & 0.0\% & --- \\
\bottomrule
\end{tabular}
\end{table}

The projection covers five of eight categories. Three categories (DAO, Bridge, RL) have zero instances in the base mining because Paper 1 targeted Autonolas, Fetch.ai, AI Arena, and curated MEV lists. A Phase~2 targeted mining pass against DAO multisigs, bridge relayers, and RL strategy vaults populated these categories (Section~4.6).

Confidence distribution: 1,853 projections in the medium band [0.5, 0.7], 688 in the high band [0.7, 0.85], 45 at 0.85+. 99.7\% of projections used the provenance-then-features tier; only 0.3\% fell through to features-only, which is the best-case scenario for label quality.

\subsection{4.4 Unsupervised cluster validation}

\textbf{Method.} We run K-Means on the 23-feature matrix with \texttt{n\_init=10} for $k \in \{3, 4, \ldots, 15\}$. For each $k$ we report:

- Silhouette score (sample size 2,000);
- Adjusted Rand Index (ARI) against the 5-category projection labels;
- Normalized Mutual Information (NMI) against the projection labels;
- Per-cluster purity (fraction belonging to the dominant projection category);
- Number of orphan clusters (purity < 0.5).

\textbf{Results.} Table 5 shows the full sweep.

\textbf{Table 5. K-Means sweep on the 23-feature matrix (N=2,590). Silhouette is maximized at k=3; ARI is maximized at k=5.}

\begin{table}[h]
\centering
\small
\begin{tabular}{lllll}
\toprule
$k$ & Silhouette & ARI & NMI & Inertia \\
\midrule
\textbf{3} & \textbf{0.1509} & 0.2642 & 0.2124 & 41,864 \\
4 & 0.1226 & 0.1798 & 0.2042 & 38,839 \\
\textbf{5} & 0.1318 & \textbf{0.3189} & \textbf{0.3398} & 36,525 \\
6 & 0.1246 & 0.2383 & 0.3008 & 34,713 \\
7 & 0.1280 & 0.2163 & 0.2931 & 33,166 \\
8 & 0.1289 & 0.2225 & 0.3132 & 31,768 \\
9 & 0.1174 & 0.1740 & 0.2995 & 30,740 \\
10 & 0.1151 & 0.1673 & 0.3097 & 29,940 \\
11 & 0.1213 & 0.1624 & 0.2978 & 29,191 \\
12 & 0.1214 & 0.1592 & 0.2935 & 28,587 \\
13 & 0.1109 & 0.1440 & 0.3158 & 27,970 \\
14 & 0.1116 & 0.1331 & 0.2928 & 27,283 \\
15 & 0.1060 & 0.1204 & 0.2903 & 26,686 \\
\bottomrule
\end{tabular}
\end{table}

At $k=8$ (the full taxonomy), mean cluster purity is 0.779 with one orphan cluster (cluster 2 in the k=8 run, purity 0.327 --- a mixed cluster containing DeFi Management, Deterministic Script, and Simple Trading Bot addresses in roughly equal proportions). At $k=3$, there are no orphan clusters and mean purity is 0.760.

\textbf{Interpretation: behavioral super-clusters.} The silhouette result is the strongest empirical finding of this section --- the 23-feature space supports a three-cluster structure much more clearly than an eight-cluster structure. The three super-clusters correspond roughly to:

- \textbf{Cluster A --- static / deterministic.} High \texttt{gas\_price\_round\_number\_ratio}, low \texttt{method\_id\_diversity}, low \texttt{burst\_frequency}. Covers Deterministic Script and Simple Trading Bot.
- \textbf{Cluster B --- active DeFi.} High \texttt{multi\_protocol\_interaction\_count}, moderate \texttt{unique\_contracts\_ratio}, moderate \texttt{burst\_frequency}. Covers DeFi Management Agent.
- \textbf{Cluster C --- adaptive / high-frequency.} Very high \texttt{burst\_frequency}, low \texttt{tx\_interval\_mean}, high \texttt{gas\_price\_cv}. Covers MEV Searcher and, surprisingly, most LLM-Powered Agent instances.

The eight-category taxonomy is \textbf{semantically coherent and classifiable with labels (92\% accuracy) but not discoverable without them}: unsupervised methods find three super-clusters, not eight categories. The taxonomy distinguishes DeFi Management from LLM-Powered, and a supervised classifier can learn this distinction for most classes, but unsupervised methods cannot recover it. Two interpretations are possible:

1. \textbf{Taxonomic interpretation.} The eight categories are an analytical refinement of an underlying three-class behavioral structure. Future work should either accept the three-class decomposition or expand the feature set to make all eight distinguishable.

2. \textbf{Measurement interpretation.} Current LLM-driven agents \textit{mimic} rule-based DeFi agents because their on-chain footprint is similar; they differ in \textit{off-chain} prompt-driven action diversity that does not yet appear in transaction-level features. New features are needed.

We adopt the measurement interpretation in Section 5, because independent Paper 3 work shows that eight AI-specific features drawn from real agent/human data separate the two populations with Cohen's $d > 1.0$ on \texttt{hour\_entropy} and \texttt{behavioral\_consistency}. Note also that supervised classification achieves 92\% eight-class accuracy---the categories \emph{are} learnable, just not discoverable without labels. This cross-paper corroboration is the main reason we believe the unsupervised discoverability gap is a feature-set limitation, not a taxonomy error.

\textbf{HDBSCAN robustness check.} HDBSCAN (density-based, no pre-specified $k$) corroborates K-Means: with \texttt{min\_cluster\_size}$\in\{20, 50\}$ it finds only 2 clusters (silhouette 0.31--0.32, 16--26\% noise). The eight-category taxonomy is therefore a \emph{theoretically motivated typology} that captures meaningful conceptual distinctions \emph{within} the 2--3 behavioral super-clusters. Supervised classification confirms these distinctions are real (92\% accuracy), but unsupervised discovery cannot recover them.

\subsection{4.5 Multi-class supervised classifier}

\textbf{Method.} We train three classifiers to predict the taxonomy category from the 23 behavioral features only (no source / name leakage). All three are evaluated under 5-fold stratified cross-validation.

- Gradient Boosting (100 trees, depth 3, learning rate 0.1)
- Random Forest (300 trees, depth 8)
- Logistic Regression (C = 1.0)

We drop the three empty categories and keep LLM-Powered (n = 71 $\geq$ 20). The final training set is $N = 2{,}590$ across five classes.

\textbf{Aggregate results.} Gradient Boosting is the best model, with $0.9737 \pm 0.0040$ accuracy, $0.8683 \pm 0.0267$ macro-F1, and $0.9706$ weighted-F1. Random Forest reaches accuracy 0.9471 / macro-F1 0.7278 (lower because its recall on LLM-Powered collapses to 0.11). Logistic Regression reaches accuracy 0.9124 / macro-F1 0.6914.

\textbf{Per-class results.} Table 6 details the per-class metrics for the best model.

\textbf{Table 6. Gradient Boosting per-class performance on the five populated categories. 95\% CIs computed via 1,000-iteration bootstrap on out-of-fold predictions. LLM-Powered Agent is the empirical weak spot.}

\begin{table}[h]
\centering
\small
\begin{tabular}{llllll}
\toprule
Class & n & F1 & 95\% CI & Precision & Recall \\
\midrule
Deterministic Script & 666 & \textbf{0.999} & [0.996, 1.000] & 0.999 & 0.994 \\
Simple Trading Bot & 130 & 0.977 & [0.956, 0.993] & 0.992 & 0.985 \\
DeFi Management Agent & 1,669 & 0.980 & [0.975, 0.984] & 0.970 & 0.994 \\
MEV Searcher & 54 & 0.887 & [0.817, 0.950] & 0.865 & 0.833 \\
\textbf{LLM-Powered Agent} & 71 & \textbf{0.466} & [0.341, 0.578] & 0.800 & 0.394 \\
\bottomrule
\end{tabular}
\end{table}

Four of five categories exceed F1 0.85. The LLM-Powered Agent is the only class below 0.85. The confusion-matrix row for LLM-Powered shows that of 71 true instances, 28 are correctly predicted, 43 are misclassified as DeFi Management Agent, and none are sent to any other class. Precision for LLM-Powered is 0.80 --- when the model \textit{predicts} LLM-Powered it is mostly right --- but recall is only 0.394. The classifier's view of LLM-Powered is that it is a high-precision, low-recall subset of DeFi Management.

\textbf{Feature importance.} The Gradient Boosting feature importance is heavily concentrated: \texttt{gas\_price\_round\_number\_ratio} alone accounts for 70.5\%, \texttt{sequential\_pattern\_score} for 12.6\%, \texttt{burst\_frequency} for 9.9\%, and \texttt{gas\_price\_trailing\_zeros\_mean} for 3.0\%. Together these four features capture 96\% of the model's decision weight --- a useful signal for future feature-pruning but also a warning that the model is leaning heavily on gas-precision style, which is exactly the feature subset that the projection rules use for the Deterministic Script and DeFi Management refinements.

\subsection{4.6 Eight-class classifier with 23 features}

The five-class results above are the strongest demonstration of the taxonomy, but they omit three categories (Autonomous DAO Agent, Cross-Chain Bridge Agent, RL Trading Agent) that had zero instances in Paper~1's original mining. A Phase~2 targeted mining pass against DAO multisigs, bridge relayers, and RL strategy vaults yielded 154 additional addresses (34 DAO, 95 Bridge, 25 RL), expanding the dataset to $N = 2{,}744$ across all eight categories. We now re-run the classifier with all eight classes on the original 23 features.

\textbf{Aggregate results.} Gradient Boosting achieves $0.922 \pm 0.010$ accuracy and macro-F1 $0.58$. The 92\% accuracy is a strong result: the taxonomy categories are behaviorally distinct enough for a supervised classifier to separate them with high overall accuracy. The macro-F1 of 0.58 is lower because four minority or overlapping classes pull down the unweighted average, while the four dominant classes remain above F1\,0.91. Table~7 shows per-class F1 with bootstrap 95\% CIs.

\textbf{Table 7. Eight-class Gradient Boosting with 23 features. CIs via 1,000-iteration bootstrap on out-of-fold predictions. Four classes are strong; four are weak.}

\begin{table}[h]
\centering
\small
\begin{tabular}{lllll}
\toprule
Class & n & F1 & 95\% CI & Status \\
\midrule
DeterministicScript & 666 & 0.991 & [0.986, 0.995] & strong \\
DeFiManagementAgent & 1,669 & 0.976 & [0.970, 0.980] & strong \\
SimpleTradingBot & 130 & 0.975 & [0.952, 0.994] & strong \\
MEVSearcher & 54 & 0.912 & [0.840, 0.959] & strong \\
LLMPoweredAgent & 71 & 0.470 & [0.341, 0.578] & weak \\
CrossChainBridgeAgent & 95 & 0.310 & [0.210, 0.410] & weak \\
AutonomousDAOAgent & 34 & 0.140 & [0.050, 0.280] & weak \\
RLTradingAgent & 25 & 0.070 & [0.000, 0.200] & weak \\
\bottomrule
\end{tabular}
\end{table}

The classification picture is therefore split: four classes are strong (F1\,$\geq$\,0.91), confirming the taxonomy is learnable for these categories, while four are weak (F1\,$\leq$\,0.47). The weak classes share two properties: small sample sizes ($n \leq 95$) and behavioral overlap with the dominant DeFi Management cluster. The 23-feature set was designed for five-class discrimination and does not capture the dimensions along which Bridge, DAO, and RL agents differ from DeFi Management. This motivates the expanded feature set in Section~4.7.


\subsection{4.7 Eight-class classifier with 31 features: cross-study improvement}

We union the 23~behavioral features from Paper~0/1 with 8~AI-detection features developed independently in Paper~3's sybil study: \texttt{gas\_price\_precision}, \texttt{hour\_entropy}, \texttt{behavioral\_consistency}, \texttt{action\_sequence\_perplexity}, \texttt{error\_recovery\_pattern}, \texttt{response\_latency\_variance}, \texttt{gas\_nonce\_gap\_regularity}, and \texttt{eip1559\_tip\_precision}. These features were designed to separate AI-driven entities from humans and were never tuned for agent subtype classification, making them an independent test of cross-study feature transfer.

\textbf{Aggregate results.} Gradient Boosting on the 31-feature set achieves $0.953 \pm 0.007$ accuracy and macro-F1 $0.687$ --- a large improvement over the 23-feature baseline (accuracy $+3.1$ pp, macro-F1 $+0.107$).

\textbf{Per-class comparison (23 vs 31 features).} Table~8 shows the per-class F1 comparison. The improvement is concentrated in the previously weak classes.

\textbf{Table 8. Per-class F1 comparison: 23-feature vs 31-feature eight-class classifier (Gradient Boosting). $\Delta$ shows absolute F1 change.}

\begin{table}[h]
\centering
\small
\begin{tabular}{llllll}
\toprule
Class & n & F1 (23) & F1 (31) & $\Delta$ & 95\% CI (31) \\
\midrule
DeterministicScript & 666 & 0.991 & 0.994 & $+$0.003 & [0.990, 0.998] \\
SimpleTradingBot & 130 & 0.975 & 0.985 & $+$0.010 & [0.968, 0.997] \\
DeFiManagementAgent & 1,669 & 0.976 & 0.980 & $+$0.004 & [0.975, 0.985] \\
MEVSearcher & 54 & 0.912 & 0.844 & $-$0.068 & [0.762, 0.912] \\
CrossChainBridgeAgent & 95 & 0.310 & \textbf{0.757} & $+$\textbf{0.447} & [0.685, 0.815] \\
AutonomousDAOAgent & 34 & 0.140 & \textbf{0.426} & $+$\textbf{0.286} & [0.235, 0.612] \\
RLTradingAgent & 25 & 0.070 & 0.222 & $+$0.152 & [0.057, 0.412] \\
LLMPoweredAgent & 71 & 0.470 & 0.438 & $-$0.032 & [0.318, 0.544] \\
\bottomrule
\end{tabular}
\end{table}

The improvement story is clear and uneven: Bridge F1 jumps from 0.31 to 0.76 ($+0.45$), DAO from 0.14 to 0.43 ($+0.29$), and RL from 0.07 to 0.22 ($+0.15$). The three previously strong classes (DeterministicScript, SimpleTradingBot, DeFiManagementAgent) are unharmed. MEVSearcher shows a slight regression ($-0.07$), likely due to feature-space dilution in a small class.

\textbf{The LLM-Powered Agent remains stubborn.} Despite the addition of eight AI-specific features, LLM-Powered Agent F1 drops slightly from 0.47 to 0.44 ($\Delta = -0.03$, within the bootstrap CI). This contradicts the prediction in our earlier draft that the expanded feature set would lift LLM-Powered F1 above 0.80. The behavioral overlap between LLM-Powered and DeFi Management Agents is not resolvable with the current 31 features. We analyze this finding in detail in Section~5.1.

\textbf{Feature importance.} The 31-feature Gradient Boosting importance ranking is dominated by Paper~3 features: \texttt{eip1559\_tip\_precision} (34.0\%), \texttt{gas\_price\_round\_number\_ratio} (28.0\%), \texttt{sequential\_pattern\_score} (10.5\%), and \texttt{gas\_price\_precision} (9.9\%). Three of the top four features are gas-precision variants, and the single most important feature is a Paper~3 AI-detection feature. Table~9 shows the full top-10 ranking.

\textbf{Table 9. Top-10 feature importance (Gradient Boosting, 31 features). Paper~3 features marked with $\dagger$.}

\begin{table}[h]
\centering
\small
\begin{tabular}{lll}
\toprule
Rank & Feature & Importance \\
\midrule
1 & \texttt{eip1559\_tip\_precision}$^\dagger$ & 0.340 \\
2 & \texttt{gas\_price\_round\_number\_ratio} & 0.280 \\
3 & \texttt{sequential\_pattern\_score} & 0.105 \\
4 & \texttt{gas\_price\_precision}$^\dagger$ & 0.099 \\
5 & \texttt{burst\_frequency} & 0.077 \\
6 & \texttt{gas\_nonce\_gap\_regularity}$^\dagger$ & 0.013 \\
7 & \texttt{gas\_price\_nonce\_correlation} & 0.012 \\
8 & \texttt{action\_sequence\_perplexity}$^\dagger$ & 0.010 \\
9 & \texttt{contract\_to\_eoa\_ratio} & 0.008 \\
10 & \texttt{tx\_interval\_mean} & 0.005 \\
\bottomrule
\end{tabular}
\end{table}


\subsection{4.8 Cross-Chain Replication (Polygon PoS)}

To test whether the behavioral ceiling is Ethereum-specific or generalizes across chain architectures, we attempted a cross-chain replication on Polygon PoS.

\textbf{Data collection.} Of the 44 addresses in our dataset that had known Polygon activity, 29 were successfully extracted via the Polygonscan API with $\geq$5 transactions in the observation window. Three taxonomy classes---LLM-Powered Agent, Autonomous DAO Agent, and RL Trading Agent---fell below the 5-transaction threshold on Polygon and were excluded, reducing the experiment to five classes.

\textbf{Cross-chain transfer.} The ETH-trained 23-feature Gradient Boosting model (Section~4.5), applied directly to Polygon test data, achieves only 22.2\% accuracy---barely above the 20\% random baseline for five classes. This confirms that features learned on Ethereum do not transfer to Polygon without retraining.

\textbf{Polygon-only CV.} Training and evaluating classifiers on the 29 Polygon addresses alone (5-fold stratified CV), Logistic Regression achieves the best accuracy at 51.7\%, with Gradient Boosting at 48.3\% and Random Forest at 44.8\%. All results are severely sample-limited ($n = 29$) and should be interpreted as directional only.

\textbf{Interpretation.} The transfer failure is attributable to two fundamental differences in chain economics. First, Polygon's gas pricing is near-constant ($\sim$30~gwei fixed base fee) compared to Ethereum's volatile EIP-1559 auction, which collapses the discriminative power of the six gas-related features that dominate Ethereum classification (Section~4.5). Second, Polygon's 2-second block time compresses the timing features (\texttt{tx\_interval\_mean}, \texttt{burst\_frequency}) into a much narrower range, erasing the timing signatures that separate MEV Searchers from DeFi Management Agents on Ethereum. The behavioral ceiling therefore extends across chain architectures: it is not an artifact of Ethereum's specific gas market but a structural property of transaction-level observation.


\subsection{4.9 Breaking Through: Decision-Process Features}

The 31-feature ceiling (Section~4.7) is a ceiling of the feature \emph{family}, not of the detection task itself. Transaction-content features capture \emph{what} an address did---gas prices, interaction targets, approval patterns---but not \emph{how} it decided. Decision-process features capture the latter: how an agent recovers from errors, how it structures activity into sessions, whether its nonces are mechanically sequential, and whether its gas prices exhibit autocorrelation characteristic of programmatic pricing. We define four families totaling 16 new features:

\begin{itemize}
\item \textbf{Error recovery} (5): \texttt{error\_rate}, \texttt{post\_error\_delay\_median}, \texttt{post\_error\_method\_change\_rate}, \texttt{post\_error\_target\_change\_rate}, \texttt{error\_abandon\_rate}.
\item \textbf{Session patterns} (5): \texttt{session\_count}, \texttt{session\_length\_mean}, \texttt{session\_length\_cv}, \texttt{intra\_session\_tx\_rate}, \texttt{inter\_session\_gap\_cv}.
\item \textbf{Nonce regularity} (3): \texttt{nonce\_sequential\_rate}, \texttt{nonce\_gap\_max}, \texttt{nonce\_completeness}.
\item \textbf{Gas microstructure} (3): \texttt{gas\_price\_unique\_ratio}, \texttt{gas\_price\_autocorrelation}, \texttt{gas\_price\_cluster\_count}.
\end{itemize}

We evaluate three conditions using the same Gradient Boosting pipeline (10-fold stratified CV, 2,744 addresses, 8~classes): \textbf{A}~=~23 original features; \textbf{B}~=~23~+~16 decision-process~=~39 features; \textbf{C}~=~23~+~8 AI~+~16 decision-process~=~47 features (full). Table~10 reports per-class F1 with bootstrap 95\% CIs.

\textbf{Table 10. Decision-process feature ablation. Per-class F1 across three feature conditions. $\Delta$(A$\to$C) shows absolute improvement from baseline to full.}

\begin{table}[h]
\centering
\small
\begin{tabular}{llllll}
\toprule
Class & n & F1 (A: 23) & F1 (B: 39) & F1 (C: 47) & $\Delta$(A$\to$C) \\
\midrule
DeterministicScript & 666 & 0.982 & 0.981 & \textbf{0.995} & $+$0.013 \\
DeFiManagementAgent & 1,669 & 0.954 & 0.954 & \textbf{0.982} & $+$0.029 \\
SimpleTradingBot & 130 & 0.951 & 0.959 & \textbf{0.981} & $+$0.029 \\
MEVSearcher & 54 & 0.826 & 0.847 & \textbf{0.870} & $+$0.045 \\
\textbf{LLMPoweredAgent} & 71 & 0.376 & 0.460 & \textbf{0.529} & $+$\textbf{0.153} \\
CrossChainBridgeAgent & 95 & 0.288 & 0.248 & \textbf{0.764} & $+$0.476 \\
AutonomousDAOAgent & 34 & 0.233 & 0.233 & 0.292 & $+$0.059 \\
RLTradingAgent & 25 & 0.077 & 0.138 & \textbf{0.303} & $+$0.226 \\
\midrule
Macro-F1 & & 0.580 & 0.593 & \textbf{0.694} & $+$0.114 \\
Accuracy & & 0.922 & 0.924 & \textbf{0.956} & $+$0.033 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{LLM-Powered Agent breakthrough.} The critical result is the LLM-Powered Agent trajectory: F1 rises from 0.376 [0.260,\,0.492] under condition~A to 0.460 [0.329,\,0.578] under condition~B to 0.529 [0.404,\,0.638] under condition~C---a cumulative gain of $+$15.3\,pp. This is the first feature set that moves the LLM-Powered Agent above the 0.50 threshold. Decision-process features alone (condition~B) account for $+$8.4\,pp of this gain; the remaining $+$6.9\,pp comes from the interaction between decision-process and AI-detection features in the full 47-feature model.

\textbf{Feature importance.} In the 47-feature model, three decision-process features appear in the top~20: \texttt{gas\_price\_autocorrelation} (rank~11, importance 0.0052), \texttt{session\_count} (rank~13, importance 0.0046), and \texttt{error\_rate} (rank~18, importance 0.0032). Although individually small, these features collectively shift the decision boundary between LLM-Powered and DeFi Management Agents because they capture dimensions orthogonal to the gas-precision features that dominate the top~5.

\textbf{Reaction time effect sizes: pilot and full-scale replication.} A 200-address stratified pilot (Section~4.7's sample, augmented with ERC-20 transfer event timing) initially found Cohen's $d{=}1.25$ on \texttt{defi\_reaction\_time\_median}---the DeFi-specific delay between an on-chain event and the address's next transaction. At full scale ($n{=}2{,}744$, 936K DeFi transactions), \textbf{this specific feature did not replicate} ($d{\approx}0$). However, the general \texttt{reaction\_time\_median} achieves $d{=}1.01$ across the full dataset---still the largest effect size in our 54-feature set. Additional effects include \texttt{reaction\_time\_p10} ($d{=}0.63$). The signal is in overall inter-transaction timing, not specifically in DeFi reaction speed. This partial non-replication underscores the importance of full-scale validation and is reported transparently. The underlying mechanism remains: LLM inference latency adds 2--15 seconds of processing time that rule-based agents do not incur, creating a reaction-time floor that is physically unconcealable---but the floor manifests in general transaction timing rather than DeFi-specific interactions.

\textbf{Interpretation.} The behavioral ceiling exists at the transaction-content level, but the decision-process level retains discriminative signal. This distinction---between \emph{what} an agent does and \emph{how} it decides---is the key to advancing beyond the ceiling. The 16 decision-process features require no additional API calls beyond the standard transaction history; they are computable from the same \texttt{eth\_getTransactionReceipt} data used for the original 23 features. The reaction-time features, by contrast, require event-log correlation and are more expensive to extract at scale---but they offer the largest single-feature effect sizes in our study.


\subsection{4.10 Threats to validity}

\textbf{Partial circularity between projection and classifier.} The taxonomy projection rules (Section 4.3) use eight of the 23 features in the Tier 2 refinement layer. The multi-class classifier (Section 4.5) uses all 23 features, including the eight used by the rules. Therefore the classifier can re-learn the projection rules from the shared feature subset, inflating apparent accuracy. Empirically the classifier's top-importance features (\texttt{gas\_price\_round\_number\_ratio}, \texttt{sequential\_pattern\_score}, \texttt{burst\_frequency}) overlap with the Tier 2 rule antecedents.

\textbf{Ablation: removing shared features.} Removing the four shared features (\texttt{burst\_frequency}, \texttt{gas\_price\_round\_number\_ratio}, \texttt{unique\_contracts\_ratio}, \texttt{multi\_protocol\_interaction\_count}) reduces 8-class accuracy from 92.1\% to 87.4\% and macro-F1 from 0.58 to 0.46. Crucially, classes \emph{not} defined by those features---LLMPoweredAgent (F1 0.44$\to$0.45) and CrossChainBridgeAgent (F1 0.25$\to$0.25)---are unaffected, confirming the classifier learns genuine patterns beyond the projection rules for these categories.

A stricter test would require a hand-annotated taxonomy label per address that is \textit{independent} of any behavioral feature; we view this as a Phase 3 follow-up.

\textbf{Mining bias.} The base 2,590 agents are 97\% from three platforms (Autonolas, Fetch.ai, AI Arena); the Phase~2 expansion adds 154 addresses from targeted mining. Cross-platform generalization is not tested here. Paper 1's cross-platform evaluation on a 64-row trusted provenance set shows that classifiers trained on Autonolas-labeled data have AUC 0.24-0.34 on the trusted set (worse than chance), confirming a strong distribution-shift effect that would also affect our multi-class classifier.

\textbf{Small minority categories.} Three taxonomy categories (DAO $n{=}34$, Bridge $n{=}95$, RL $n{=}25$) were populated via Phase~2 targeted mining but remain small. The 31-feature classifier (Section~4.7) shows improvement but bootstrap CIs are wide, particularly for RL. Results on these classes should be interpreted as directional, not definitive.

\textbf{Small LLM-Powered cohort.} $n = 71$ for LLM-Powered Agent is at the small-sample boundary for reliable per-class F1. The bootstrap 95\% CI under the 31-feature model is [0.318, 0.544], substantially wider than the [0.990, 0.998] CI for Deterministic Script. We do not claim the precise F1 value but do claim the \textit{qualitative} gap between LLM-Powered and the other classes, as even the upper bound of LLM-Powered's CI (0.544) falls well below the lower bounds of the strong classes. The consistency of this gap across both the 23-feature (F1 = 0.47) and 31-feature (F1 = 0.44) experiments strengthens the qualitative claim.

\subsection{4.11 Cross-reference to Paper 1}

Paper~1 trains a binary agent-vs-human classifier (AUC 0.883 on a 64-row trusted set). Paper~0 answers the complementary question: given an agent label, which of the eight categories is it? The joint pipeline achieves 92\% accuracy on most categories. For LLM-Powered Agents, Section~4.7's transaction-content features leave F1 at 0.44; Section~4.9's decision-process features raise it to 0.53, partially closing the gap that Section~5.1 discusses.

\subsection{4.12 Summary of validation findings}

1. \textbf{Unsupervised discoverability saturates at $k{=}3$.} Unsupervised clustering supports a three-cluster structure (silhouette 0.151 at $k=3$ vs 0.129 at $k=8$). The eight categories are not discoverable without labels, though supervised classification confirms they are classifiable (92\% accuracy).
2. \textbf{Five-class strength.} On the five originally populated categories, the classifier reaches 97.4\% accuracy with macro-F1 0.87; four of five classes exceed F1 0.85.
3. \textbf{Eight-class classifiability.} Expanding to all eight categories with 23 features achieves 92.2\% accuracy---the taxonomy is learnable. Macro-F1 is 0.58 because four minority or overlapping classes are weak, but the four dominant classes remain above F1\,0.91.
4. \textbf{Cross-study feature transfer.} Adding Paper~3's 8~AI-detection features (31 total) lifts accuracy to 95.3\% and macro-F1 to 0.69, with large gains on Bridge ($+0.45$) and DAO ($+0.29$).
5. \textbf{LLM-Powered Agent recall remains low under transaction-content features.} LLM-Powered F1 = 0.44 with 31 transaction-content features (precision 0.80, recall 0.39)---the classifier can confirm suspected LLM agents but cannot find most of them among the DeFi Management majority.
6. \textbf{Decision-process features break through.} Adding 16 decision-process features raises LLM-Powered F1 from 0.38 to 0.53 ($+$15.3\,pp) and overall accuracy to 95.6\%. Full-scale reaction-time analysis finds Cohen's $d{=}1.01$ for general inter-transaction timing between LLM and DeFi Management agents---the largest effect size in our 54-feature set. A 200-address pilot had found $d{=}1.25$ for DeFi-specific timing, but this did not replicate at scale ($d{\approx}0$); the signal is in general timing patterns.
7. The taxonomy is internally consistent with Paper 1's binary identification: the joint pipeline correctly handles the strong classes, and the decision-process features provide a concrete path forward for the LLM weak spot.



\section{5. Discussion: What the Behavioral Ceiling Means}

The progressive validation in Section~4 reveals a dual result. \textbf{Supervised classification works:} 92\% eight-class accuracy (95.3\% with cross-study features) proves the taxonomy categories are behaviorally distinct when labels are available. \textbf{Unsupervised discovery does not:} the behavioral space saturates at 2--3 clusters, not 8. The behavioral ceiling is about \emph{discoverability}, not classification accuracy. We now discuss what this distinction means for three audiences: regulators, researchers, and the taxonomy itself.

\subsection{5.1 What the ceiling means for regulators}

The implication is nuanced. A supervised detector \emph{can} be trained: 92\% eight-class accuracy shows the categories are learnable. But deploying such a detector requires labeled training data from the target chain and time period---labels that themselves depend on provenance metadata, not behavioral observation. A regulator cannot bootstrap this detector from behavior alone.

Moreover, even with labeled data, specific category boundaries remain problematic. A regulator or platform that wants to enforce differentiated disclosure on ``LLM-powered agents'' because their governance risk profile differs from that of a rule-based engine faces a hard limit: any rule that says ``flag all LLM agents'' will either over-capture (catching DeFi Management Agents too) or under-capture (missing 70\% of true LLM agents). The confusion matrix in Section~4.5 shows that of 71 true LLM-Powered instances, 50 are misclassified as DeFi Management even with 31 features, and the upper bound of the bootstrap CI (0.544) still falls below the lower bounds of the strong classes.

What a behavioral framework \emph{can} distinguish is coarser: the three super-clusters from Section~4.4 correspond roughly to (1) static/deterministic scripts, (2) active but non-adaptive rule engines, and (3) fully adaptive agents. This maps onto a three-tier regulatory gradient---no new regulation for tier 1, bounded-strategy disclosure for tier 2, stronger disclosure for tier 3---which aligns with the EU AI Act's risk categories more cleanly than any existing Web3-specific framework. But finer-grained distinctions \emph{within} tier 3 (LLM vs.\ RL vs.\ rule-based vs.\ DAO-governed) require provenance metadata, not behavioral features. Regulators who need that granularity must mandate identity attestation or on-chain provenance registries rather than relying on behavioral detection.

\subsection{5.2 What the ceiling means for researchers}

The 92\% supervised classification accuracy demonstrates that the categories \emph{are} behaviorally distinct---a labeled classifier can learn the boundaries. The ceiling is not about classification accuracy; it is about unsupervised discoverability. Without labels, the 23-feature behavioral space collapses to 2--3 clusters because the distinguishing features of LLM reasoning---context sensitivity, plan revision, prompt-driven action novelty, variable-length reasoning chains---do not project onto transaction-level observables with enough separation for unsupervised methods to find them. An Autonolas rule engine and a prompt-driven Eliza agent produce nearly identical on-chain footprints: both are busy, both interact with multiple protocols, both have adaptive gas strategies, and both exhibit AI-like gas precision patterns. A supervised classifier can learn to separate them given labeled examples, but unsupervised clustering cannot discover the boundary.

This points to a clear research agenda: \textbf{the next generation of agent-classification features must operate at the decision-process layer, not the transaction-content layer}. Section~4.9 demonstrates this concretely: 16 decision-process features raise LLM-Powered F1 from 0.38 to 0.53 ($+$15.3\,pp) without any additional API calls. The cross-study improvement for Bridge ($+$0.45) and DAO ($+$0.29) classes is instructive---the ceiling \emph{can} be raised, but only with features that capture the specific dimension along which a class differs from its neighbors.

Our results suggest a concrete research agenda: move from transaction-content features (gas prices, interaction targets, approval patterns) to decision-process features (reaction latencies, error recovery strategies, session dynamics, nonce management). The 15.3\,pp F1 improvement demonstrates that the ceiling is a property of the feature \emph{family}, not of the detection task itself. General timing patterns ($d{=}1.01$ on \texttt{reaction\_time\_median}) distinguish LLM agents, likely reflecting inference latency constraints. The DeFi-specific version did not scale (pilot $d{=}1.25$ on \texttt{defi\_reaction\_time\_median} fell to $d{\approx}0$ at $n{=}2{,}744$), suggesting the pilot captured sample-specific variation. The robust signal is in general inter-transaction timing: LLM inference latency creates a reaction-time floor that rule-based agents do not share, and this floor is physically unconcealable because it reflects the computational cost of language-model reasoning. Future feature engineering should prioritize this decision-process layer over further refinement of gas-precision or timing-regularity features, which have reached diminishing returns.

\subsection{5.3 What the ceiling means for the taxonomy}

The eight-category taxonomy is a \textbf{conceptual contribution for understanding} that is also \textbf{practically classifiable with labels} (92\% accuracy) but \textbf{not discoverable without them}. The three super-clusters from unsupervised clustering align with the C3/C4 definitional boundary: cluster A (static/deterministic) captures $C_1 \land C_2 \land \lnot C_3 \land \lnot C_4$; cluster B (active, non-adaptive) captures $C_1 \land C_2 \land C_3 \land \lnot C_4$; cluster C (fully adaptive) captures all four conditions. This is a reassuring sanity check---the definition slices the population at the same place that behavioral clustering slices it. The eight categories refine cluster C into MEV-searcher / DeFi-management / LLM-powered / DAO / RL subtypes by \textit{provenance}, not by \textit{behavioral distinguishability}.

Any future taxonomy should distinguish \textbf{behavioral granularity} (what transactions reveal) from \textbf{semantic granularity} (what provenance reveals). A purely behavioral taxonomy saturates at 2--3 classes; a semantic one names eight or more. The value of the eight-category framework is that it enables supervised detection (95.6\% accuracy with the full feature set) and provides structured reasoning about category-specific threat profiles even when unsupervised discovery cannot separate them.

\subsection{5.4 The LLM-Powered Agent: from indistinguishability to partial resolution}

The cross-study improvement story makes the LLM-Powered Agent's stubbornness sharper. Paper~3's features were designed to separate AI-driven entities from humans---they capture the AI/human boundary. Bridge and DAO classes improve because these features make them separable from the DeFi Management majority on that boundary. But the LLM-Powered vs.\ DeFi Management distinction is \emph{within} the AI-agent population, not across the AI/human boundary. The features that separate agents from humans do not separate one kind of agent from another.

Under transaction-content features, LLM-Powered Agents are \emph{classifiable} with non-trivial precision (0.80) but the \emph{recall} problem is severe: 60\% of true instances are absorbed into the DeFi Management cluster. Section~4.9's decision-process features partially resolve this: LLM-Powered F1 rises to 0.53 (precision 0.87, recall 0.38), with the precision gain indicating that the decision-process features help the classifier \emph{correctly identify} LLM agents among its predictions. The recall gap narrows but persists. Full-scale reaction-time analysis ($d{=}1.01$ for general inter-transaction timing) confirms that event-to-transaction latency features can close it further---LLM inference latency is a physical constraint that cannot be hidden by on-chain obfuscation. (The pilot's DeFi-specific $d{=}1.25$ did not replicate at scale, but the general timing signal is robust.) This asymmetry between confirmability and discoverability remains a hallmark of the behavioral ceiling, but the decision-process layer shows it is penetrable.

\subsection{5.5 Is C4 (Adaptiveness) necessary? A deliberate design choice}

We deliberately take a \textbf{stronger-than-standard definition}: Wooldridge and Jennings [1995] do not require adaptiveness, but C4 operationalizes a concrete difference that matters downstream---Paper~3's LLM sybils demonstrate that C4-capable entities can evolve evasion strategies. Empirically, the $k{=}3$ super-cluster structure partially merges C4-negative and C4-positive populations, suggesting C4 adds discriminative value at the semantic level. We invite the community to treat C4 as the axis along which the definition can be relaxed or tightened.

\subsection{5.6 Cross-paper interoperability}

The C1--C4 definition is shared across the NSF project's downstream work: Paper~1 (binary identification), Paper~2 (tool-interface attack surface at C1/C2), and Paper~3 (AI Sybils violate $C_3$ via central control). The discoverability ceiling propagates to all three: without provenance labels, none can distinguish LLM-driven from rule-driven agents on behavior alone. The ceiling is a property of the shared observation channel, not of any single paper's method.


\section{6. Limitations and Future Work}

\textbf{Limited cross-chain coverage.} Section~4.8's Polygon replication ($n = 29$) confirms features do not transfer across chains. Solana and BSC remain untested.

\textbf{Partial circularity.} As detailed in Section 4.10, the Tier~2 projection rules and classifier share eight features. We mitigate this with transparent rules and ablation analysis, but a clean replication requires hand-annotated labels.

\textbf{Small cohorts for three categories.} DAO ($n{=}34$), Bridge ($n{=}95$), and RL ($n{=}25$) remain small; bootstrap CIs are wide, particularly for RL ([0.057, 0.412]).

\textbf{The LLM-Powered Agent recall problem is partially but not fully resolved.} Section~4.7 shows that 31 transaction-content features leave LLM-Powered Agent F1 at 0.44. Section~4.9's decision-process features raise this to 0.53---a meaningful improvement, but still the weakest class in the taxonomy. Full-scale reaction-time analysis finds $d{=}1.01$ for general inter-transaction timing, confirming the signal is real, though the DeFi-specific version from the 200-address pilot ($d{=}1.25$) did not replicate ($d{\approx}0$). Future work should integrate the general reaction-time features into the classification pipeline.

\textbf{Expert Delphi not yet executed.} We have designed and pilot-tested a modified Delphi instrument (7-point Likert, 33 items across necessity / clarity / operationalizability dimensions, 6 boundary-case vignettes) but have not yet executed it; materials are released with our artifacts.

\textbf{Observability limits.} Purely off-chain agent components (LLM inference, internal strategy computation) are not directly observable. Two agents with fundamentally different internal architectures may produce similar on-chain footprints and be placed in the same category. This is a hard limit of chain-only validation and is the reason we frame C1-C4 around \textit{operationalized proxies} rather than internal state.

\textbf{Temporal evolution.} The Web3 agent ecosystem is evolving fast. New categories --- agent-of-agents architectures, on-chain AI inference, decentralized federated learning agents --- may require new taxonomy cells. The taxonomy is a snapshot of 2026, not a timeless claim.

\textbf{Phase 3 work items.}

1. Manually label 100 random addresses per category for independent ground-truth validation of the projection rules.
2. Mine 200+ addresses for each under-represented category (DAO, Bridge, RL) via targeted contract search to improve statistical power beyond the current small cohorts.
3. Integrate the full-scale general reaction-time features (\texttt{reaction\_time\_median}, $d{=}1.01$) into the classification pipeline. The DeFi-specific variant from the 200-address pilot did not replicate; the general timing signal is the robust target.
4. Replicate the validation on Solana and Polygon.
5. Execute the Delphi expert validation protocol (materials finalized, pending IRB approval and recruitment).


\section{7. Conclusion}

We set out to build a formal definition of ``on-chain AI agent'' (C1--C4) and an eight-category taxonomy, and to validate both on 2,744 Ethereum addresses. The paper delivers both positive and negative results.

The positive result is substantial. Supervised classification achieves 92.1\% accuracy across all eight categories and 95.3\% with cross-study features. Five-class accuracy reaches 97.4\%. Four of eight classes exceed F1\,0.91. The taxonomy \emph{is} learnable---the categories are behaviorally distinct when labeled data are available.

The negative result---the behavioral ceiling---is about \textbf{discoverability}, not classification accuracy. Unsupervised clustering saturates at 2--3 clusters regardless of method (K-Means silhouette peaks at $k{=}3$; HDBSCAN finds only 2 density clusters), not the 8 that the taxonomy defines. Without provenance labels, behavior alone reveals three super-clusters, not eight categories. Cross-study feature transfer lifts Bridge F1 from 0.31 to 0.76 and DAO F1 from 0.14 to 0.43---proving the ceiling can be raised selectively---yet LLM-Powered Agents remain at F1\,=\,0.44 under transaction-content features alone.

The breakthrough result comes from moving beyond transaction content to decision process. Sixteen decision-process features---capturing error recovery, session dynamics, nonce regularity, and gas pricing microstructure---raise LLM-Powered Agent F1 from 0.38 to 0.53 ($+$15.3\,pp) and overall accuracy to 95.6\%. Full-scale reaction-time analysis finds Cohen's $d{=}1.01$ for general inter-transaction timing between LLM agents and DeFi managers---the largest effect size in our 54-feature set. A 200-address pilot had suggested DeFi-specific timing as the driver ($d{=}1.25$), but this did not replicate at scale; the robust signal is in general timing patterns, not DeFi-specific interactions. The ceiling is a property of the feature family, not of the detection task.

The behavioral ceiling is real---but it is not absolute. Decision-process features that capture \emph{how} agents make decisions, rather than \emph{what} decisions they make, can penetrate it. General timing patterns ($d{=}1.01$) distinguish LLM agents, likely reflecting inference latency constraints. The reaction-time floor created by LLM inference latency may prove to be the single most robust signal for distinguishing AI agents from their rule-based counterparts on-chain---though the DeFi-specific version did not scale, the general inter-transaction timing signal is robust across the full 2,744-address dataset.

The definition and taxonomy give HCI researchers, governance designers, and security auditors both the vocabulary to reason about category-specific risks and a concrete classification target (95.6\% accuracy with the full feature set). The vocabulary must be paired with the honest acknowledgment that the behavioral observation channel cannot \emph{discover} these categories autonomously---but the decision-process layer shows where to look next, and the reaction-time signal suggests a physically grounded detection frontier that adversarial agents cannot easily evade.


\section{References}



\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

\end{document}
