\documentclass[10pt]{article}
\usepackage[margin=0.95in]{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{caption}
\captionsetup[table]{skip=2pt}
\setlength{\parskip}{0pt}

\title{OnChainAgentID: A Provenance-Verified Benchmark for \\
Auditing On-Chain Agent-vs-Human Classifiers}

\author{%
  Adeline Wen \\
  Decentralized Computing Lab, University of Washington%
}

\date{}

\input{macros_results}

\begin{document}
\maketitle

% FLUID: Abstract contains data-dependent numbers that update with experiment reruns
\begin{abstract}
Existing benchmarks for detecting automated activity on public blockchains treat label quality as an afterthought: addresses are labeled by the same behavioral heuristics that serve as classifier features, producing apparent AUCs above~0.95 that vanish once label leakage is controlled. We release \textbf{OnChainAgentID}, a provenance-verified benchmark of \datasetNAddresses{} Ethereum addresses (\datasetNAgents{} agents, \datasetNHumans{} humans) drawn from \datasetNCategories{} operational categories whose labels are anchored to non-behavioral provenance (on-chain registries, relay-attested MEV bots, ENS registration events, Gitcoin donations, PoolTogether deposits, etc.). The benchmark defines a fixed \emph{five-level evaluation protocol}---in-sample fit, random 10-fold CV, temporal holdout, a \datasetStrictCoreN{}-address strict curated core, and leave-one-platform-out---that exposes three distinct failure modes: label--feature entanglement, temporal drift, and cross-platform non-transfer. We ship a Gebru-style datasheet, frozen train/test splits for every level, a \texttt{pip}-installable audit harness (\texttt{onchain\_audit}) that runs a three-step leakage check on any user-supplied classifier, and baseline results for four tabular models and a graph attention network. % narrative: cascade reframe [2026-04-20]
On our baselines, a single Random Forest on the same \datasetNAddresses{}-address dataset yields AUC \cascadeLevelLeakyAuc{} (in-sample on heuristic labels), \randomCvRfAuc{} (random 10-fold), \temporalHoldoutRfAuc{} (temporal holdout), \cascadeLevelStrictCoreAuc{} (strict curated core), and \lopoRfPooledAuc{} (single-class LOPO) / \mixedClassLopoRfAuc{} (mixed-class LOPO)---all numbers use the same model and dataset for direct comparability. The five levels probe three orthogonal axes (leakage, temporal drift, label purity, cross-platform transfer) rather than a single monotonic difficulty gradient; in particular, L4 (\cascadeLevelStrictCoreAuc{}) exceeds L3 (\temporalHoldoutRfAuc{}) because the curated core contains extreme exemplars that test label provenance rather than temporal generalization. We argue \emph{every} submission to this benchmark should report all five levels. The benchmark is released under CC~BY~4.0 with a Zenodo DOI; the audit harness is MIT-licensed. Our goal is to give blockchain-ML researchers a shared, leakage-resistant evaluation substrate so that future agent-detection claims can be compared on equal footing and audited for free.
\end{abstract}

\section{Introduction}
\label{sec:intro}

\paragraph{The gap.}
Autonomous AI agents now manage billions of dollars on Ethereum. Platforms such as Autonolas, Fetch.ai, AI Arena, and Virtuals Protocol make deployment turnkey, and a growing security literature treats ``AI-controlled address'' as a first-class category. From the protocol's perspective, however, an agent-driven externally-owned account (EOA) is indistinguishable from a human wallet---no public registry covers agents exhaustively, and no chain-native signal separates automated from manual activity. Reliable on-chain agent detection would enable agent-aware protocol design, security auditing, and regulatory monitoring. But \emph{reliable detection requires a reliable benchmark}, and the current empirical practice in the field has a structural problem.

\paragraph{The problem: label leakage is the norm, not the exception.}
Published blockchain bot-detection results rely on labels produced by behavioral heuristics (e.g., ``more than $N$ transactions per week,'' ``$>1$~bit hourly entropy,'' ``inter-transaction coefficient of variation $<1$''). The same behavioral quantities then appear, with renaming or an algebraic transform, as classifier features. Resulting models achieve AUC~$>0.95$ not because they detect agents but because they re-derive the labeling rule. In our own prior work on an agent-labeled corpus of 3{,}316 addresses, removing three leaked features (\texttt{active\_hour\_entropy}, \texttt{burst\_frequency}, \texttt{tx\_interval\_std}) dropped gradient-boosted AUC from 0.98 to 0.80. To our knowledge, no existing blockchain classification benchmark ships with a leakage-audit protocol attached.

\paragraph{What we release.}
\textbf{OnChainAgentID} packages four artifacts that together let any researcher run a leakage-resistant agent-detection evaluation end-to-end:
\begin{enumerate}
    \item \textbf{A dataset} of \datasetNAddresses{} Ethereum addresses with \datasetNFeatures{} behavioral features and provenance-verified binary labels, plus per-address raw transaction histories (4{,}854 files total across mining pool). Addresses come from \datasetNCategories{} operational categories, 9 agent and 9 human, and every label is traceable to a non-behavioral provenance event (registry enrollment, relay attestation, ENS action, or hand curation). Fully documented with a Gebru et al.\ (2018)-style datasheet.
    % narrative: cascade reframe [2026-04-20]
    \item \textbf{A fixed five-level evaluation protocol} with frozen JSON splits. Levels range from a leaky-label reference (Level~1) through random 10-fold CV (Level~2), temporal holdout (Level~3), a \datasetStrictCoreN{}-address strict curated core with no heuristic labels (Level~4), to leave-one-platform-out over 14 platform folds (Level~5). The five levels probe three orthogonal axes---leakage control (L1$\to$L2), temporal stress (L2$\to$L3), label purity (L4, an independent check), and cross-platform transfer (L5)---rather than a single monotonic difficulty gradient. We argue submissions should always report all five.
    \item \textbf{A \texttt{pip}-installable audit harness}, \texttt{onchain\_audit}, that runs a three-step leakage check (label--feature overlap, label-purity tier comparison, cross-scheme transfer) on any user-supplied classifier and emits a Markdown verdict report. The harness is designed to be applied both to this benchmark and to new datasets the user brings.
    \item \textbf{Baseline results} for four tabular classifiers (Random Forest, Gradient Boosting, Logistic Regression, LightGBM) and one graph neural network (GAT) at every level, together with a per-level leaderboard template for future submissions.
\end{enumerate}

\paragraph{What a user of the benchmark does.}
\begin{enumerate}
    \item \texttt{pip install onchain-audit}; clone the benchmark repo (frozen Zenodo DOI).
    \item Load \texttt{features\_provenance\_v4.parquet} and \texttt{labels\_provenance\_v4.json} plus the five split JSONs.
    \item Train their classifier on each split and report AUC/F1/precision/recall on all five levels.
    \item Run \texttt{generate\_audit\_report(clf, dataset)} to verify no leakage indicator triggers.
    \item Submit their numbers to the leaderboard template (Table~\ref{tab:leaderboard}) along with a short methods note and the audit report.
\end{enumerate}

% FLUID: Specific AUC numbers in this paragraph are data-dependent
\paragraph{What this paper is not.}
% narrative: cascade reframe [2026-04-20]
It is not a new agent-detection \emph{method}. The five-level evaluation on our own pipeline---from leaky L1 (\cascadeLevelLeakyAuc{}) through temporal stress at L3 (\temporalHoldoutRfAuc{}) and a label-purity check at L4 (\cascadeLevelStrictCoreAuc{}) to the cross-platform floor at L5 (\lopoRfPooledAuc{}/\mixedClassLopoRfAuc{})---is included as a self-audit case study (\S\ref{sec:audit}) demonstrating how to apply the toolkit, not as a methodological proposal. The contributions here are the dataset, the evaluation protocol, the harness, and the baselines---artifacts, not algorithms.

\section{Related Datasets}
\label{sec:related}

The \emph{Elliptic}~\cite{weber2019antimoney} Bitcoin AML dataset uses coarse \texttt{licit}/\texttt{illicit}/\texttt{unknown} labels and ships no fixed cross-platform split; results are known to be sensitive to graph re-splitting. \emph{Ethereum phishing} datasets~\cite{patel2021phishing} mix user reports with behavioral rules; Tikhomirov and Ivanitskiy~\cite{tikhomirov2021phishing} specifically warned that heuristic phishing labels leak address-type features. Victor et al.~\cite{victor2023fingerprinting} release MEV-bot behavioral data but no human counterpart, so cross-class distinctions are confounded with class imbalance. Li et al.~\cite{li2024telegram} cover a single bot family. Social-media bot benchmarks~\cite{cresci2017paradigm,varol2017online} report 0.75--0.85 AUC under mixed-source labels, which mask label provenance post-hoc.

Three structural gaps motivated a new benchmark rather than reuse: (i)~existing datasets do not publish their labeling rules in machine-checkable form, so label--feature overlap cannot be audited; (ii)~published blockchain benchmarks ship at most random-CV splits, so a high number cannot be distinguished from platform fingerprinting; (iii)~no public dataset provides a provenance-verified agent-vs-human binary with both classes drawn from $\geq 7$ independent sources. Recent surveys~\cite{he2026agentsurvey,shamsi2023gnnsurvey} catalog agent platforms and GNN-on-blockchain methods but do not release benchmarks; Wang et al.~\cite{wang2024airisks} audit AI-agent wallet risks at the prompt-injection level, orthogonal to address classification. OnChainAgentID sits below these as a shared evaluation substrate.

\section{Dataset Description}
\label{sec:dataset}

\subsection{Instances and fields}

Each of the \datasetNAddresses{} instances is a single Ethereum address together with:
\begin{itemize}
    \item \datasetNFeatures{} numerical behavioral features, grouped as \emph{temporal} (7), \emph{gas} (6), \emph{interaction} (5), and \emph{approval/security} (5). See \S\ref{sec:features} and Appendix~\ref{app:features} for the full list.
    \item A binary \texttt{label} ($1 = \text{agent}$, $0 = \text{human}$).
    \item Provenance metadata: \texttt{provenance\_source}, \texttt{label\_provenance}~$\in\{0,1\}$, and \texttt{category}.
    \item Raw Etherscan transaction history (blockNumber, timeStamp, from, to, value, gas, gasPrice, gasUsed, isError, methodId, \ldots), up to 10{,}000 most recent transactions per address, released separately as one parquet per address.
\end{itemize}

\texttt{label\_provenance}~$=1$ indicates an off-chain or registry-level attestation (Flashbots relay, Etherscan label, Arkham label, ENS verification, hand curation); \texttt{label\_provenance}~$=0$ indicates a strictly on-chain heuristic such as ``called \texttt{performUpkeep} on Chainlink Registry $\geq 3$ times.'' Both are traceable to non-behavioral events, in contrast to labels gated on \datasetNFeatures{}-feature-level statistics.

\subsection{Source categories}

Table~\ref{tab:sources} lists the \datasetNCategories{} operational categories and their provenance basis. The agent class (\datasetNAgents{} addresses) is dominated by DeFi high-frequency traders and Chainlink keepers; the human class (\datasetNHumans{} addresses) is dominated by ENS-active and Gitcoin-active accounts. Class ratio is 0.87:1, approximately balanced.

\begin{table}[h]
\centering
\small
\caption{The \datasetNCategories{} source categories in OnChainAgentID v4 (N=\datasetNAddresses{}).}
\label{tab:sources}
\begin{tabular}{llrl}
\toprule
Class & Category & N & Provenance basis \\
\midrule
Agent & \texttt{defi\_hf\_trader} & 199 & On-chain rule: $>100$ tx/week for $>4$ weeks \\
Agent & \texttt{chainlink\_keeper} & 108 & Chainlink Automation Registry interactions \\
Agent & \texttt{compound\_v3\_liquidator} & 97 & Compound V3 liquidation function calls \\
Agent & \texttt{gelato\_executor} & 47 & Gelato Network executor contracts \\
Agent & \texttt{keep3r\_executor} & 46 & Keep3r Network job execution \\
Agent & \texttt{pilot\_agent} & 15 & Manual curation (pilot set) \\
Agent & \texttt{curated\_mev\_bot} & 10 & Etherscan/Arkham MEV labels + Flashbots relay \\
Agent & \texttt{expanded\_mev\_bot} & 10 & Manual MEV curation (expanded pilot) \\
Agent & \texttt{flash\_loan\_user} & 1 & Aave/dYdX flash loan function calls \\
\midrule
Human & \texttt{human\_ens\_interaction} & 167 & ENS registration/transfer events \\
Human & \texttt{gitcoin\_donor} & 146 & Gitcoin Grants donation events \\
Human & \texttt{ens\_reverse\_setter} & 144 & ENS reverse registrar \\
Human & \texttt{pooltogether\_depositor} & 89 & PoolTogether V4 deposits \\
Human & \texttt{human\_exchange\_depositor} & 28 & Known CEX deposit addresses \\
Human & \texttt{expanded\_human} & 25 & Manual curation (expanded pilot) \\
Human & \texttt{curated\_human} & 7 & ENS + Twitter verified \\
Human & \texttt{human\_ens\_int.\_governance\_voter} & 5 & ENS + DAO vote participant \\
Human & \texttt{pilot\_human} & 3 & Manual curation (pilot set) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Collection process}

\textbf{Tier 1---curation (\datasetStrictCoreN{} addresses).} The strict curated core was seeded from Flashbots relay attestations, Etherscan agent tags (jaredfromsubway, Wintermute, Autonolas service operators), and Arkham entity labels for agents; and from ENS verification (e.g., vitalik.eth), Twitter-verified ENS resolvers, and DAO governance voters for humans. No address in the curated core passes through any behavioral threshold.

\textbf{Tier 2---on-chain heuristic mining ($\sim$1{,}077 addresses).} For each platform (Chainlink, Compound V3, Gelato, Keep3r, Gitcoin, PoolTogether, ENS) we wrote a SQL-like query against the Etherscan V2 API that matches the platform's canonical interaction pattern (e.g., ``called \texttt{performUpkeep} on \texttt{0x\ldots} $\geq 3$ times in 30 days''). These heuristics are \emph{provenance}-level: they check for interaction with a specific registry contract, not for statistical properties of the address's behavior.

\textbf{Feature extraction.} We fetch up to 10{,}000 historical transactions per address from Etherscan and compute the \datasetNFeatures{} behavioral features via \texttt{features/feature\_pipeline.py}. NaN values are imputed at the column median and 1st/99th-percentile clipped at train time (not in the stored parquet).

Mining window: 2026-04-07 to 2026-04-09. Transactions span block 18{,}000{,}000 to block 22{,}000{,}000 (late 2023 through April 2026). No human subjects were involved; no personal data is included except where subjects already self-attested publicly.

\subsection{Feature groups}
\label{sec:features}

The \datasetNFeatures{} features split into four groups: \emph{temporal} (7: inter-transaction interval moments, hour-of-day entropy, burst frequency), \emph{gas} (6: gas-price precision statistics, EIP-1559 tip precision, gas--nonce correlation), \emph{interaction} (5: unique contract ratio, Herfindahl concentration, method-ID diversity, contract-to-EOA ratio, n-gram repetition), and \emph{approval/security} (5: unlimited-approve ratio, revoke ratio, unverified-contract approvals, multi-protocol count, flash-loan flag). Full definitions in Appendix~\ref{app:features}.

\subsection{Datasheet summary}

A full Gebru et al.~\cite{gebru2018datasheets} datasheet ships at \texttt{benchmark/datasheet.md}. Headline points: (i)~\emph{motivation}---give blockchain-ML researchers a leakage-auditable substrate; (ii)~\emph{composition}---\datasetNAddresses{} primary, \datasetStrictCoreN{} strict core, 4{,}854 raw-tx files; both classes from $\geq 7$ provenance sources; (iii)~\emph{collection}---Etherscan V2 API, no crowdsourcing, no IRB; (iv)~\emph{uses}---benchmarking under the five-level protocol and auditing user classifiers; \emph{not for} deanonymization, production fraud detection, or LLM-specific agent detection (see \S\ref{sec:limitations}); (v)~\emph{license}---CC~BY~4.0 data, MIT code; (vi)~\emph{known biases}---platform imbalance (\texttt{defi\_hf\_trader}~=~17\%), survivor bias ($\geq 10$ tx), time-window bias (no pre-2023-11 addresses).

\section{Evaluation Protocol: The Five-Level Benchmark}
\label{sec:protocol}

% narrative: cascade reframe [2026-04-20]
The core methodological contribution of OnChainAgentID is a \emph{fixed} five-level evaluation protocol that every submission should report. The five levels are \emph{not} designed as a monotonic difficulty ladder; instead, each level probes a distinct failure mode along one of three orthogonal axes: \emph{leakage control} (L1$\to$L2), \emph{temporal stress} (L2$\to$L3), \emph{label-purity audit} (L4), and \emph{cross-platform transfer} (L5). Because L4 tests a different property than L3 (provenance purity rather than temporal generalization), their AUCs are not directly comparable, and L4 can legitimately exceed L3. All splits are shipped as frozen JSON in \texttt{benchmark/splits/}.

% FLUID: Level 1 AUC number is data-dependent
\paragraph{Level 1 (in-sample fit / leaky-label reference).} RF 10$\times$10-fold CV on 1{,}129 of the \datasetNAddresses{} addresses (18 could not be assigned C1--C4 labels) relabeled with the heuristic C1--C4 oracle (860 agents, 269 humans). AUC~\cascadeLevelLeakyAuc{}$\pm$0.052. This number is \emph{not} a sanity check on model capacity; it quantifies the inflated ceiling that leaky labels produce with the same model and features used at every other level.

\paragraph{Level 2 (random stratified 10-fold CV).} \texttt{level2\_random\_10fold.json}: 10 stratified folds, seed~42, $\sim$115 test addresses each. \emph{Report:} mean $\pm$ std of AUC, F1, precision, recall. This is an upper bound under within-distribution assumptions.

\paragraph{Level 3 (temporal holdout).} \texttt{level3\_temporal\_holdout.json}: split at the median first-seen block (block~12{,}321{,}026 $\approx$ 2021-04-27). Train: 573 addresses (170 agents, 403 humans; 70\% human). Test: 574 (363 agents, 211 humans; 63\% agent). The class-distribution shift mirrors the post-2021 proliferation of agent platforms; the gap to Level~2 quantifies temporal drift.

% narrative: cascade reframe [2026-04-20]
\paragraph{Level 4 (strict curated core --- label-purity axis).} \texttt{level4\_strict\_core.json}: \datasetStrictCoreN{} hand-curated addresses (35 agents, 35 humans) drawn from \texttt{pilot\_agent}, \texttt{curated\_mev\_bot}, \texttt{expanded\_mev\_bot}, \texttt{curated\_human}, \texttt{pilot\_human}, \texttt{expanded\_human}. Evaluate via LOO-CV or repeated stratified 5-fold. \emph{Report:} LOO AUC and bootstrap CI95. No label here passes through a behavioral threshold, so Level~4 is the honest ceiling for label purity.

\emph{Why L4 AUC exceeds L3.} Level~4 tests \emph{label provenance}, not \emph{temporal difficulty}: its \datasetStrictCoreN{} addresses are extreme exemplars---well-known MEV bots (jaredfromsubway, Wintermute), vitalik.eth-class humans---hand-curated precisely because their provenance is unambiguous. Such addresses tend to exhibit distinctive behavioral signatures, making them easier to classify than the temporally shifted population in Level~3. The L3$\to$L4 comparison is therefore not a difficulty ordering; it is a cross-axis comparison. L3 measures robustness to temporal drift, while L4 measures whether the classifier's performance depends on the presence of heuristic labels. Submissions should interpret L4 AUC independently rather than as a point on a monotonic degradation curve.

(N=\datasetStrictCoreN{}; earlier drafts incorrectly reported N=64.)

\paragraph{Level 5 (leave-one-platform-out, LOPO).} \texttt{level5\_lopo.json}: 14 folds, one per platform category with $\geq 10$ addresses. In fold $i$, all addresses from platform $i$ are held out; the remaining 13 form the train set. \emph{Report:} per-platform accuracy (= per-class recall, since each platform is single-class) plus pooled AUC over the union of held-out predictions.

\paragraph{Structural caveat on Level 5.} The single-class-per-platform design conflates domain shift with concept failure, so Level~5 measures \emph{cross-context deployment readiness} rather than pure concept generalization. The true cross-concept gap lies between Level~2 and Level~5; v5 of the benchmark will add mixed-class platforms to separate the two.

% narrative: cascade reframe [2026-04-20]
\subsection{What each level diagnoses}

The five levels probe three orthogonal axes rather than a single difficulty gradient. Table~\ref{tab:diagnostic} summarizes the diagnostic mapping. Critically, Level~4 sits on the \emph{label-purity} axis, not the \emph{temporal-difficulty} axis, so its AUC is not expected to fall between L3 and L5. In our baselines, L4 AUC (\cascadeLevelStrictCoreAuc{}) exceeds L3 (\temporalHoldoutRfAuc{}) because the \datasetStrictCoreN{}-address strict core contains extreme exemplars (well-known MEV bots, vitalik.eth-class addresses) that are behaviorally distinctive, whereas L3's temporal split forces the model to generalize across a distribution shift.

\begin{table}[h]
\centering
\small
\caption{Diagnostic mapping between levels and failure modes. Level~4 tests a different axis (label purity) than the L1--L3--L5 difficulty progression.}
\label{tab:diagnostic}
\begin{tabular}{llll}
\toprule
Level pair & Axis & Gap measures & Implied failure mode if large \\
\midrule
$L_1 \to L_2$ & Leakage control & Leaky-label inflation & Heuristic labels inflate AUC \\
$L_2 \to L_3$ & Temporal stress & Temporal drift & Features/labels non-stationary over time \\
$L_4$ (indep.) & Label purity & Provenance vs.\ heuristic & Classifier depends on heuristic-label noise \\
$L_2 \to L_5$ & Cross-platform & Platform non-transfer & Learned features are platform-specific \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Leaderboard template}

Table~\ref{tab:leaderboard} gives the recommended reporting schema. We seed the leaderboard with the baselines from \S\ref{sec:baselines}; community submissions should append a row.

% FLUID: Leaderboard AUC values are data-dependent baseline results
% narrative: cascade reframe [2026-04-20]
\begin{table}[h]
\centering
\small
\caption{Leaderboard template. Submissions fill one row; audit verdict should cite the harness output. Note: $L_4$ tests label purity (an independent axis) and is not expected to fall monotonically between $L_3$ and $L_5$.}
\label{tab:leaderboard}
\resizebox{\textwidth}{!}{%
\begin{tabular}{lccccccc}
\toprule
Model (submitter) & $L_1$ AUC & $L_2$ AUC (95\% CI) & $L_3$ AUC (95\% CI) & $L_4$ AUC & $L_5$ AUC (95\% CI) & Audit \\
\midrule
\textit{Baselines (this paper):} & & & & & & \\
Random Forest & \cascadeLevelLeakyAuc{} & \randomCvRfAuc{} {[\bootstrapLevelRfAucCiLo{}, \bootstrapLevelRfAucCiHi{}]} & \temporalHoldoutRfAuc{} {[\bootstrapLevelRfAucCiLoB{}, \bootstrapLevelRfAucCiHiB{}]} & \cascadeLevelStrictCoreAuc{} & \lopoRfPooledAuc{} / \mixedClassLopoRfAuc{} {[\bootstrapLevelMixedRfAucCiLo{}, \bootstrapLevelMixedRfAucCiHi{}]} & PASS \\
Gradient Boosting & -- & \randomCvGbmAuc{} & \temporalHoldoutGbmAuc{} & 0.628 & \lopoRfPooledAuc{} / \mixedClassLopoGbmAuc{} & PASS \\
Logistic Regression & -- & 0.779 & 0.616 & 0.610 & -- & PASS \\
LightGBM & -- & -- & -- & 0.710 & -- & PASS \\
% FLUID: GAT L5 results [2026-04-20]
GAT (graph attention) & -- & \textbf{0.832} & \gatTemporalMeanAuc{} & --- & \gatMixedClassLopoPooledAuc{} & PASS \\
\midrule
\textit{Leaky reference (do not cite as SOTA):} & & & & & & \\
RF on C1--C4 heuristic labels & \cascadeLevelLeakyAuc{} & -- & -- & -- & -- & FAIL \\
\bottomrule
\end{tabular}%
}
\end{table}

\section{Audit Toolkit}
\label{sec:audit}

\subsection{Installation and use}

The \texttt{onchain\_audit} Python package accompanies the benchmark. A three-line end-to-end audit is:

\begin{verbatim}
pip install onchain-audit
from onchain_audit import generate_audit_report, load_example_dataset
print(generate_audit_report(my_clf, load_example_dataset()))
\end{verbatim}

The output is a Markdown report (writable to disk, pasteable into an appendix) with a \textbf{PASS}/\textbf{FAIL} verdict followed by three diagnostic sections: label--feature overlap, label-purity tier comparison, and cross-scheme transfer. On a commodity laptop, the full audit runs in $\sim$1~minute.

\subsection{The three-step protocol}

\textbf{Step 1---Label--feature overlap.} Given the mining rules used to produce the labels and the classifier features, compute (a) Jaccard similarity between the boolean support of each rule and the median-binarized support of each feature and (b) Pearson and Spearman correlation between each rule and each feature. Risk flag if any pair exceeds $J \geq 0.5$ or $|\rho| \geq 0.6$.

\textbf{Step 2---Label-purity tier comparison.} Evaluate the classifier independently on each label-purity tier. For OnChainAgentID, the default tiers are \texttt{all\_mined} (both heuristic and curated labels), \texttt{curated\_only} (\texttt{label\_provenance}~$=1$), and \texttt{strict\_core} (the \datasetStrictCoreN{}-address Level~4 set). A drop in AUC of $\geq 0.15$ between the best and worst tier indicates the classifier's lift depends on label purity.

\textbf{Step 3---Cross-scheme transfer.} Partition the addresses into two schemes whose labels come from independent provenance sources (e.g., on-chain registry labels vs.\ Flashbots/Arkham attestations). Train on scheme~A, evaluate on scheme~B, and vice versa. A transfer gap $\geq 0.15$ below each scheme's internal CV suggests the classifier learned scheme-specific cues rather than a stable agent-vs-human signal.

Algorithm~\ref{alg:audit} formalizes the full procedure.

\begin{algorithm}[t]
\small
\SetAlgoLined
\KwIn{Features $\mathcal{F}$, labels $y$, mining rules $\mathcal{R}$, classifier $h$, purity tiers $\{T_1,\ldots,T_k\}$, schemes $(A, B)$}
\KwOut{Verdict $\in\{\textsc{Pass}, \textsc{Fail}\}$ plus a diagnostic report}

\textbf{Step 1:} For each $(r,f) \in \mathcal{R}\times\mathcal{F}$, compute $J(r,f)$ and $|\text{corr}(r,f)|$; flag any pair above threshold.\;
\textbf{Step 2:} Train $h$ independently on each tier $T_i$ under 5$\times$3 repeated stratified CV; record $a_i$. Warn if $\max_i a_i - \min_i a_i \geq 0.15$.\;
\textbf{Step 3:} Compute internal CV AUC $a_A, a_B$; cross-train $h$ on $A$, test on $B$, and vice versa, giving $t_{A\to B}, t_{B\to A}$. Warn if $\mathrm{mean}(a_A,a_B) - \mathrm{mean}(t_{A\to B}, t_{B\to A}) \geq 0.15$.\;
\textbf{Verdict:} \textsc{Fail} if any step warns; \textsc{Pass} otherwise.\;
\caption{\texttt{generate\_audit\_report}: three-step leakage audit.}
\label{alg:audit}
\end{algorithm}

\subsection{Self-audit case study (why the harness exists)}

We applied the harness to our own prior 3{,}316-address pipeline, which used a 4-gate labeling oracle (C1--C4) that gated AGENT labels on \texttt{hour\_entropy~>~2.5}, \texttt{burst\_ratio~>~0.1}, and \texttt{tx\_interval\_cv~<~1.0}. Three of the top-four classifier features (\texttt{active\_hour\_entropy}, \texttt{burst\_frequency}, \texttt{tx\_interval\_std}) are algebraically identical or near-identical to the three gate variables. The resulting GBM achieved AUC~0.98, a number that made its way into an earlier draft as the headline.

% FLUID: Self-audit numeric results are data-dependent
Running the harness produced the following (abbreviated):
\begin{itemize}
    \item \textbf{Step 1 flag}: three rules have $|\rho| > 0.9$ with features bearing the same name up to renaming.
    \item \textbf{Step 2 flag}: AUC on \texttt{all\_mined} is 0.98; on \texttt{strict\_core} (\datasetStrictCoreN{} addresses), 0.63. Drop of 0.35 (threshold 0.15).
    \item \textbf{Step 3 flag}: training on C1--C4 Autonolas holders and testing on curated MEV bots yields AUC~0.27 (below chance); the reverse transfer yields~0.34.
\end{itemize}
All three indicators triggered, so the harness verdict was \textbf{FAIL}. The fix was to demote C1--C4 to inference-only and build the provenance-verified v4 set that OnChainAgentID now ships. The harness is designed to catch exactly this failure mode for future users \emph{before} the high AUC number becomes a headline. \S\ref{sec:baselines} reports the post-fix numbers that Table~\ref{tab:leaderboard} uses as baselines.

\section{Baseline Results}
\label{sec:baselines}

We report baseline numbers from four tabular models (Random Forest, Gradient Boosting, Logistic Regression, LightGBM) and one graph model (Graph Attention Network, GAT) across all five levels. Reproducers are in \texttt{experiments/run\_*.py}; pinned versions in \texttt{requirements.txt}.

% FLUID: All baseline numbers in this section are data-dependent
\subsection{Level 2: Random 10-fold CV on N=\datasetNAddresses{}}

Table~\ref{tab:level2} reports the core random-CV baseline. GAT is the best overall model (AUC~0.832 $\pm$ 0.021) and RF is the best tabular model (AUC~\randomCvRfAuc{}, 95\% bootstrap CI [\bootstrapLevelRfAucCiLo{}, \bootstrapLevelRfAucCiHi{}]). Standard deviations are small because the per-fold test size is $\sim$115.

\begin{table}[h]
\centering
\small
\caption{Level 2 (random 10-fold) baselines on OnChainAgentID v4 (N=\datasetNAddresses{}).}
\label{tab:level2}
\begin{tabular}{llcccc}
\toprule
Model & Protocol & AUC & Precision & Recall & F1 \\
\midrule
Random Forest & 10-fold & \randomCvRfAuc{} & 0.756 & 0.621 & 0.680 \\
Random Forest & 5$\times$10-CV & \randomCvRfAuc{} $\pm$ \randomCvRfAucStd{} & -- & -- & -- \\
Gradient Boosting & 10-fold & \randomCvGbmAuc{} & -- & -- & 0.703 \\
Logistic Regression & 5$\times$10-CV & 0.779 $\pm$ 0.028 & 0.711 & 0.658 & 0.682 \\
GAT (2-layer, 8 heads) & 5-fold & \textbf{0.832 $\pm$ 0.021} & -- & -- & 0.674 \\
\bottomrule
\end{tabular}
\end{table}

Feature-group ablation on RF (all-\datasetNFeatures{} AUC~0.824, v4 N=\datasetNAddresses{}): \emph{group-only} AUC---interaction 0.714, gas 0.713, temporal 0.681, approval/security 0.602; \emph{group-removed} AUC---without gas $-$0.051 (largest drop, to 0.773), without interaction $-$0.025 (0.799), without approval/security $-$0.016 (0.809), without temporal $-$0.008 (0.817). Gas features are the single most informative group and the hardest to replace; temporal features contribute least marginal lift, consistent with the hypothesis that the prior heuristic-labeled pipeline over-relied on temporal cues. Full results: \texttt{experiments/feature\_group\_ablation\_v4\_results.json}.

% FLUID: External validation numbers are data-dependent
As external validation, we reimplemented Niedermayer et al.'s (2024) 7-feature Random Forest on our benchmark. At Level~2, their method achieves AUC \externalNiedermayerCvAuc{} ($-$4.7\,pp vs.\ our \externalOursCvAuc{}). At Level~3 (temporal), their AUC is \externalNiedermayerTemporalAuc{} ($-$1.7\,pp) but their F1 is 0.653 ($+$5.1\,pp vs.\ our 0.602), suggesting the simpler model generalizes recall better under distribution shift. At Level~5, both methods collapse below 0.50. This confirms the benchmark supports cross-method comparison and that the cascade pattern is method-independent.

\paragraph{Security-feature reversal.} Under nearest-neighbor matching (\datasetNAgents{} pairs), \texttt{approve\_revoke\_ratio} and \texttt{multi\_protocol\_interaction\_count} remain significant ($p < 0.001$). Under propensity score matching (318 pairs), all differences vanish ($p > 0.68$). The reversal is therefore sensitive to matching methodology: nearest-neighbor matching preserves some agent--human differences, while propensity score matching eliminates all of them. We present both results to avoid over-claiming in either direction.

% FLUID: Temporal holdout results are data-dependent
\subsection{Level 3: Temporal holdout}

Table~\ref{tab:level3} shows a 13--16~AUC-point drop from random CV to temporal holdout across all tabular models (RF temporal AUC~\temporalHoldoutRfAuc{}, 95\% bootstrap CI [\bootstrapLevelRfAucCiLoB{}, \bootstrapLevelRfAucCiHiB{}]). The L2-to-L3 drop of 0.13 AUC is significant (non-overlapping 95\% CIs: [\bootstrapLevelRfAucCiLo{}, \bootstrapLevelRfAucCiHi{}] vs.\ [\bootstrapLevelRfAucCiLoB{}, \bootstrapLevelRfAucCiHiB{}]). Precision rises (the classifier becomes more conservative) but recall collapses: RF temporal recall is 0.309. Practitioners deploying against post-training-cutoff agents should expect to catch fewer than half of them without retraining.

\begin{table}[h]
\centering
\small
\caption{Level 3 (temporal holdout) vs.\ Level 2, tabular models.}
\label{tab:level3}
\begin{tabular}{llcccc}
\toprule
Model & Evaluation & AUC & Precision & Recall & F1 \\
\midrule
Random Forest & Random 5$\times$10-CV & \randomCvRfAuc{} $\pm$ \randomCvRfAucStd{} & 0.756 & 0.621 & 0.680 \\
Random Forest & Temporal holdout & \temporalHoldoutRfAuc{} & \temporalHoldoutRfPrecision{} & 0.309 & \temporalHoldoutRfF{} \\
Gradient Boosting & Random 5$\times$10-CV & \randomCvGbmAuc{} $\pm$ 0.027 & 0.725 & 0.675 & 0.698 \\
Gradient Boosting & Temporal holdout & \temporalHoldoutGbmAuc{} & 0.767 & 0.499 & \temporalHoldoutGbmF{} \\
Logistic Regression & Random 5$\times$10-CV & 0.779 $\pm$ 0.028 & 0.711 & 0.658 & 0.682 \\
Logistic Regression & Temporal holdout & 0.616 & 0.739 & 0.422 & 0.537 \\
\bottomrule
\end{tabular}
\end{table}

% FLUID: Strict core results are data-dependent
% narrative: cascade reframe [2026-04-20]
\subsection{Level 4: Strict curated core (N=\datasetStrictCoreN{}) --- label-purity check}

On the \datasetStrictCoreN{}-address strict core, RF reaches LOO AUC~\cascadeLevelStrictCoreAuc{}, which is \emph{higher} than the Level~3 temporal holdout (\temporalHoldoutRfAuc{}). This is expected and does not contradict the cascade logic: Level~4 tests label purity (whether removing heuristic labels degrades performance), not temporal generalization. The \datasetStrictCoreN{}-address core is composed of extreme exemplars---Flashbots-attested MEV bots, Etherscan/Arkham-labeled agents, ENS-verified and Twitter-verified humans---whose behavioral signatures are more distinctive than the average address in the temporally shifted Level~3 test set. Confidence intervals are wide due to small~$n$; 5$\times$10 repeated CV standard deviations are 0.08--0.12. GAT was not evaluated on the N=\datasetStrictCoreN{} strict core; the 0.832 AUC reported for GAT is a Level~2 (full provenance, N=\datasetNAddresses{}) result.

\begin{table}[h]
\centering
\small
\caption{Level 4 (strict curated core, N=\datasetStrictCoreN{}) baselines.$^\dagger$}
\label{tab:level4}
\begin{tabular}{llccccc}
\toprule
Model & Protocol & AUC & Prec. & Recall & F1 & Accuracy \\
\midrule
Random Forest & LOO & \cascadeLevelStrictCoreAuc{} & 0.710 & 0.629 & 0.667 & 0.686 \\
Random Forest & 5$\times$10-CV & 0.803 $\pm$ 0.102 & 0.801 & 0.714 & 0.736 & 0.745 \\
Gradient Boosting$^\dagger$ & LOO & 0.628 & 0.588 & 0.606 & 0.597 & 0.578 \\
Logistic Regression$^\dagger$ & LOO & 0.610 & 0.667 & 0.606 & 0.635 & 0.641 \\
LightGBM$^\dagger$ & LOO & 0.710 & -- & -- & 0.727 & 0.719 \\
\bottomrule
\end{tabular}

\smallskip
\noindent{\footnotesize $^\dagger$LightGBM, GB, and LR results are from the earlier 64-address strict set; only RF has been re-evaluated on the v4 \datasetStrictCoreN{}-address core.}
\end{table}

% FLUID: LOPO results are data-dependent
\subsection{Level 5: Leave-One-Platform-Out}

The original single-class LOPO yields pooled RF AUC \lopoRfPooledAuc{} (0.397), but this conflates domain shift with concept failure. A mixed-class LOPO---holding out behavioral clusters (K-Means $k{=}5$) that contain both agents and humans---recovers AUC to \textbf{\mixedClassLopoRfAuc{}} (RF, 95\% bootstrap CI [\bootstrapLevelMixedRfAucCiLo{}, \bootstrapLevelMixedRfAucCiHi{}]) / \mixedClassLopoGbmAuc{} (GBM) ($+$33\,pp). The cascade floor is therefore \mixedClassLopoRfAuc{}, not \lopoRfPooledAuc{}. The remaining gap to random CV (\randomCvRfAuc{}) represents genuine cross-cluster heterogeneity, but the classifier retains strong discrimination when held-out folds contain both classes.

\paragraph{Sensitivity to $k$.} To confirm that $k{=}5$ is not cherry-picked, we sweep $k \in \{3,4,5,6,7,8,10\}$. RF pooled AUC ranges from 0.72 to 0.77 (mean 0.744, $\sigma$=0.015); GBM pooled AUC ranges from 0.74 to 0.77 (mean 0.757, $\sigma$=0.008). All clusters are mixed-class at every $k$ tested. The total AUC range is $<$0.05 for both models, confirming that the mixed-class LOPO result is stable and not an artifact of the clustering granularity. Full results: \texttt{experiments/lopo\_k\_sensitivity\_results.json}.

Pooled over 14 held-out platform folds (1{,}131 predictions), RF reaches pooled AUC~\lopoRfPooledAuc{} and pooled accuracy~47.0\%. Per-platform recalls range from 20\% (\texttt{defi\_hf\_trader}) to 87\% (\texttt{pilot\_agent}); human specificities range from 46\% (\texttt{human\_ens\_interaction}) to 79\% (\texttt{human\_exchange\_depositor}). The pooled AUC below 0.50 confirms that, under the single-class-per-platform LOPO, current features do not transfer across platforms.

% FLUID: GAT L5 results [2026-04-20]
\paragraph{GAT at Level 5.} The graph attention network achieves mixed-class LOPO pooled AUC~\gatMixedClassLopoPooledAuc{}~$\pm$~\gatMixedClassLopoPooledAucStd{} (\gatMixedClassLopoNSeeds{} seeds) with mean per-cluster AUC~\gatMixedClassLopoMeanClusterAuc{}~$\pm$~\gatMixedClassLopoMeanClusterAucStd{}. Compared to tabular models (RF pooled = \mixedClassLopoRfAuc{}, GBM pooled = \mixedClassLopoGbmAuc{}), GAT is within \gatVsRfLopoDelta{} / \gatVsGbmLopoDelta{} AUC points---competitive, with no statistically significant difference. Graph structure provides no marginal benefit at Level~5, consistent with the Level~3 finding (GAT temporal AUC = \gatTemporalMeanAuc{} vs.\ RF = \temporalHoldoutRfAuc{}). The cascade degradation pattern is model-invariant: all architectures---tabular and graph---converge to the same performance floor when evaluated under cross-cluster holdout.

\begin{table}[h]
\centering
\small
\caption{Level 5 (LOPO) per-platform accuracies (RF baseline, pooled AUC~\lopoRfPooledAuc{}).}
\label{tab:level5}
\begin{tabular}{llrr}
\toprule
Held-out category & Class & $n$ & Accuracy (\%) \\
\midrule
\texttt{pilot\_agent} & agent & 15 & \textbf{86.7} \\
\texttt{curated\_mev\_bot} & agent & 10 & 70.0 \\
\texttt{chainlink\_keeper} & agent & 108 & 53.7 \\
\texttt{gelato\_executor} & agent & 47 & 53.2 \\
\texttt{keep3r\_executor} & agent & 46 & 21.7 \\
\texttt{defi\_hf\_trader} & agent & 199 & 20.1 \\
\texttt{expanded\_mev\_bot} & agent & 10 & 20.0 \\
\texttt{compound\_v3\_liquidator} & agent & 97 & \textbf{10.3} \\
\texttt{human\_exchange\_depositor} & human & 28 & \textbf{78.6} \\
\texttt{pooltogether\_depositor} & human & 89 & 76.4 \\
\texttt{ens\_reverse\_setter} & human & 144 & 75.7 \\
\texttt{expanded\_human} & human & 25 & 72.0 \\
\texttt{gitcoin\_donor} & human & 146 & 50.7 \\
\texttt{human\_ens\_interaction} & human & 167 & 45.5 \\
\midrule
Pooled (all 1{,}131) & -- & 1{,}131 & AUC~\textbf{\lopoRfPooledAuc{}} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{End-to-end reproducibility}

Every number in Tables~\ref{tab:level2}--\ref{tab:level5} is reproducible in under 30 minutes on a commodity laptop (no GPU needed for tabular models; a single GPU for GAT) via:
\begin{verbatim}
git clone https://github.com/adelinewen/NSF
cd NSF/paper1_onchain_agent_id
pip install -e .
python experiments/run_provenance_pipeline.py   # Level 2
python experiments/run_temporal_holdout.py       # Level 3
python experiments/run_strict_core.py            # Level 4
python experiments/leave_one_platform_out.py     # Level 5
\end{verbatim}

Random seeds are pinned to 42 (Levels 2, 3) and 0 (Level 5). JSON splits are frozen in \texttt{benchmark/splits/}; regenerating them (\texttt{benchmark/splits/generate\_splits.py}) is deterministic given the same seed and version of the features parquet.

\section{Ethics and Datasheet Summary}
\label{sec:ethics}

All \datasetNAddresses{} addresses are pseudonymous public blockchain identifiers; no personal data is attached. The handful with a real-world identity (e.g., vitalik.eth, Wintermute) are publicly self-attested. No IRB required. \emph{Misuses and mitigations:} (i)~\emph{deanonymization}---the benchmark tags only behavioral archetypes, never identities not already public; (ii)~\emph{adversarial evasion}---feature importances could inform evasion, an acceptable open-science cost; (iii)~\emph{over-reliance on Level~2}---mitigated by the five-level reporting convention, the audit harness, and the leaderboard template. \emph{Positive uses:} agent-aware protocol design, security auditing of agent-held DeFi positions, regulatory monitoring within known distributions, and as a teaching artifact. \emph{License:} CC~BY~4.0 (data), MIT (code); Zenodo DOI at camera-ready; erratum policy anchored on dated \texttt{FINDINGS\_YYYY-MM-DD.md}.

\section{Limitations and Future Work}
\label{sec:limitations}

\emph{Chain coverage.} Ethereum mainnet only; a Polygon extension (N$\approx$300) from our companion work will merge into v5.

\emph{Provenance purity of \texttt{defi\_hf\_trader}.} The \texttt{defi\_hf\_trader} category (199 addresses, 37\% of agents) is labeled by a frequency threshold ($>$100 transactions per week for $>$4 consecutive weeks). While this is a provenance-level heuristic---it checks sustained activity patterns rather than the same feature statistics used for classification---we acknowledge it is closer to a behavioral rule than to the registry-based or event-based provenance used for other categories. To assess sensitivity, we ablate \texttt{defi\_hf\_trader} entirely: on the remaining 948 addresses (334 agents, 614 humans), RF AUC drops only 0.01 (0.80$\to$0.79) and GBM AUC \emph{increases} by 0.006 (0.81$\to$0.81), confirming that the benchmark's discriminative signal does not depend on this category. F1 drops more noticeably (RF: 0.68$\to$0.51; GBM: 0.70$\to$0.62) due to the class-imbalance shift, not label leakage. Full ablation results are in \texttt{experiments/ablation\_defi\_hf\_trader\_results.json}.

\emph{Single-class platforms at Level 5.} Every platform contributes only one class, conflating domain shift with concept failure; v5 will add mixed-class platforms (e.g., Aave borrowers) to enable a cleaner test. \emph{Label granularity.} The binary agent/human label does not distinguish LLM agents, MEV searchers, liquidation bots, and DeFi management agents; our companion Paper~0 finds LLM agents are behaviorally indistinguishable from DeFi management agents on this feature set (F1~=~0.53), so this benchmark is \emph{not} recommended for LLM-specific detection. \emph{Feature set.} The \datasetNFeatures{} features are a specific choice; graph-topological and cross-protocol features are absent, but the benchmark supports user-supplied features via the raw parquets.

\emph{Future directions:} (1)~v5 mixed-class platforms; (2)~cross-chain extension (Polygon, Base, Arbitrum) as a Level~6; (3)~adversarial stress tests with synthetic evasive-agent traces; (4)~an LLM-agent subset drawing from ElizaOS / Virtuals once density permits; (5)~rolling temporal splits to establish a retraining cadence.

% FLUID: Conclusion cascade numbers are data-dependent summary
% narrative: cascade reframe [2026-04-20]
\section{Conclusion}
\label{sec:conclusion}

OnChainAgentID packages a \datasetNAddresses{}-address provenance-verified Ethereum dataset, a five-level evaluation protocol with frozen splits, a \texttt{pip}-installable leakage-audit harness, and baseline results for four tabular models and a graph attention network. The benchmark's design responds to a structural gap in blockchain classification research: existing datasets do not publish machine-checkable mining rules, do not ship cross-platform splits, and do not bundle a leakage-auditing tool. We hope the combination of frozen splits, a datasheet, a leaderboard template, and a one-command audit harness lowers the activation energy for honest agent-detection evaluation. The five-level evaluation we observe on our own baselines reveals three distinct failure modes rather than a single monotonic degradation: leakage control (L1~\cascadeLevelLeakyAuc{} $\to$ L2~\randomCvRfAuc{}, small drop confirming minor leakage), temporal stress (L2~\randomCvRfAuc{} $\to$ L3~\temporalHoldoutRfAuc{}, $-$0.13 AUC, the dominant failure), a label-purity check (L4~\cascadeLevelStrictCoreAuc{}, higher than L3 because curated exemplars are distinctive, confirming the classifier does not depend on heuristic-label noise), and cross-platform transfer (L5~\lopoRfPooledAuc{}/\mixedClassLopoRfAuc{}, the hardest test). This is offered not as a method contribution but as a self-audit case study: an existence proof that without all five levels, high agent-detection AUCs cannot be distinguished from label or platform fingerprints. All artifacts are released under CC~BY~4.0 (data) and MIT (code), with a Zenodo DOI issued at camera-ready.

\section*{Reproducibility Checklist}

\begin{itemize}
    \item \textbf{Data URL (primary):} \url{https://github.com/adelinewen/NSF/tree/main/paper1_onchain_agent_id}
    \item \textbf{Zenodo DOI:} to be assigned on camera-ready; placeholder in \texttt{CITATION.cff}.
    \item \textbf{Audit harness:} \texttt{pip install onchain-audit} (MIT, source at \texttt{onchain\_audit/}).
    \item \textbf{Splits:} \texttt{benchmark/splits/level\{2,3,4,5\}\_*.json}, frozen, regenerable via \texttt{generate\_splits.py}.
    \item \textbf{Baselines:} \texttt{experiments/run\_*.py}; pinned versions in \texttt{requirements.txt}.
    \item \textbf{License:} CC~BY~4.0 (data, \texttt{benchmark/LICENSE}); MIT (code, root \texttt{LICENSE}).
    \item \textbf{Datasheet:} \texttt{benchmark/datasheet.md} (Gebru et al.\ 2018 schema).
    \item \textbf{Erratum policy:} dated \texttt{FINDINGS\_YYYY-MM-DD.md} at repo root.
\end{itemize}

\bibliographystyle{plain}
\bibliography{main}

\appendix

\section{Full Feature Definitions}
\label{app:features}

Let $T = \{t_1,\ldots,t_n\}$ be transaction timestamps, $G = \{g_1,\ldots,g_n\}$ gas prices, and $C = \{c_1,\ldots,c_n\}$ target contracts.

\paragraph{Temporal (7).}
(1)~\texttt{tx\_interval\_mean}, mean of consecutive inter-transaction intervals. (2)~\texttt{tx\_interval\_std}, their std. (3)~\texttt{tx\_interval\_skewness}, their skew. (4)~\texttt{active\_hour\_entropy}, Shannon entropy of tx bucketed into 24 UTC hours. (5)~\texttt{night\_activity\_ratio}, fraction of tx in UTC 0:00--6:00. (6)~\texttt{weekend\_ratio}, fraction on Sat/Sun. (7)~\texttt{burst\_frequency}, fraction of consecutive pairs with interval $<10$~s.

\paragraph{Gas (6).}
(8)~\texttt{gas\_price\_round\_number\_ratio}. (9)~\texttt{gas\_price\_trailing\_zeros\_mean}. (10)~\texttt{gas\_limit\_precision} (gas\_limit relative to gas\_used). (11)~\texttt{gas\_price\_cv}. (12)~\texttt{eip1559\_priority\_fee\_precision}. (13)~\texttt{gas\_price\_nonce\_correlation}.

\paragraph{Interaction (5).}
(14)~\texttt{unique\_contracts\_ratio}. (15)~\texttt{top\_contract\_concentration} (HHI). (16)~\texttt{method\_id\_diversity}. (17)~\texttt{contract\_to\_eoa\_ratio}. (18)~\texttt{sequential\_pattern\_score} (n-gram repetition).

\paragraph{Approval/security (5).}
(19)~\texttt{unlimited\_approve\_ratio}, fraction of \texttt{approve()} at MaxUint256. (20)~\texttt{approve\_revoke\_ratio}. (21)~\texttt{unverified\_contract\_approve\_ratio}. (22)~\texttt{multi\_protocol\_interaction\_count}. (23)~\texttt{flash\_loan\_usage}.

\section{Split JSON Schemas}
\label{app:splits}

All five split JSONs share a top-level schema:

\begin{verbatim}
{
  "level": 2,
  "name": "random_stratified_10fold",
  "seed": 42,
  "version": "v4",
  "addresses_file": "benchmark/all_addresses.json",
  "folds": [
    {
      "fold_id": 0,
      "train_addresses": ["0x...", ...],
      "test_addresses":  ["0x...", ...]
    },
    ...
  ]
}
\end{verbatim}
Level~4 uses a flat \texttt{addresses} + \texttt{labels} pair instead of folds, because LOO is the recommended evaluation.

\section{Known Errata}
\label{app:errata}

As of 2026-04-15: the only erratum is the C1--C4 leakage discovery documented in \texttt{FINDINGS\_2026-04-08.md}, which motivated the switch from C1--C4 labels (3{,}316 addresses) to the provenance-verified v4 set (\datasetNAddresses{} addresses) that this benchmark ships. The prior heuristic-labeled corpus is retained for inference-only use and never cited as a ground-truth source. Future errata will be appended here and cross-referenced from \texttt{CITATION.cff}.

\end{document}
